---
title: 'SF: Read and preprocess raw stretch force measurements'
author: "Yaromir Kobikov <kobikov.yaromir@gmail.com>"
date: "11/26/2021"
output:
 word_document: default
 html_document:
  toc: true
  toc_float:
   collapsed: false
editor_options:
 chunk_output_type: inline
---

```{r setup, include=FALSE}

source("../BayesianPValue.R")

```

The resistance was measured as the amount of mechanical work $W_{contra}$ and $W_{ipsi}$ to stretch the contra- and ipsilesional hindlimbs, where $W(T_{0-2}) = \int_{t=0}^{2} f(t)$ was stretching  force integrated over stretching distance interval from 0 to 10 mm. Asymmetry was assessed as the contra-/ipsilesional asymmetry index $AI_W = log2(W_{contra} / W_{ipsi})$, and as the difference in work performed by the contra- and ipsilesional hindlimb $\Delta W = (W_{contra} - W_{ipsi})$. The control intact rat showed symmetric $W$ pattern; the $W$ for the left and right limbs were calculated instead of $W_{contra}$ and $W_{ipsi}$ for this animal.

## Read stretch force (SF) data 

Read raw sampled forces and match them with rat's descriptions

```{r read_write_all_files_sf_data, echo=FALSE}

PATH_FOLDER_FORCE_MEASUREMENT <- "../data/force_measurement/" 
PATH_SF_DATA_CSV <- paste0(PATH_FOLDER_FORCE_MEASUREMENT, "sf_data.csv")
PATH_DESCRIPTION <- paste0(PATH_FOLDER_FORCE_MEASUREMENT, "master-20210108_ch.xlsx")

SHEET <- "MasterFile" # for description

TEST_ROWS <- 106128 + 11*18*201 # SO + UBI + ADX
TEST_ROWS_AFTER_MERGE <- 212256 + 11*18*402

read.StretchForce <- function(RatFile, show=TRUE) {

  ratName <- sub("-RD-ForceMeasurement.xlsx", "", basename(RatFile), fixed = TRUE)
  sheetNames <- RatFile %>% 
    excel_sheets() %>% 
    as_tibble %>% 
    filter(grepl(pattern = "F([0-9]+)", value))
  
  df <- 
    map_df(
      .x = sheetNames$value, 
      ~read_excel(path = RatFile, sheet = .x, range = cell_cols("A:C")),
      .id = "replication"
      ) %>% 
    mutate(RatID = ratName) %>% 
    relocate(RatID, .before = replication)
  
  if(show) print(paste0(ratName, " -> ", toString(count(sheetNames)$n), ", ", count(df)$n))
  
  return(df)
}

correctDate <- Vectorize(function(date, pattern, sep="-") {
  
  dateSplit <- str_split(date, pattern)[[1]]

  return(paste0(dateSplit[1], sep, dateSplit[2], sep, dateSplit[3]))
  
})

my.rwData <- function() {
  
  if(file.exists(PATH_SF_DATA_CSV)) {
    print(paste0("File ", " - ", PATH_SF_DATA_CSV, " - exists"))
    return(read_csv(PATH_SF_DATA_CSV, show_col_types = FALSE))
  }
  print("In process...")
  
  sf <- 
    map_df(
      .x = list.files(path = PATH_FOLDER_FORCE_MEASUREMENT, pattern = "*-RD-ForceMeasurement.xlsx", full.names = TRUE),
      ~read.StretchForce(.x)
    )
  
  if(count(sf)$n == TEST_ROWS) print(paste0(TEST_ROWS, " - ", "OK"))

  # match rat's description with raw force measurements 
  rats_description <- 
    read_excel(PATH_DESCRIPTION, SHEET) %>%
    select(RatID, `Exp. date`, `Body weight (g)`, Day, Operation, `Operation side`, `Treatment 1`, `Treatment 2`, `Measuerment method`) %>%
    filter(`Measuerment method` == "MP") %>%
    mutate(
      Day = replace(Day, which(is.na(Day)), mean(Day, na.rm=TRUE)),
      Date = as.numeric(as.Date(correctDate(`Exp. date`, "\\."))),
      DateD = Date - min(Date)
    ) %>% 
    rename(weight = `Body weight (g)`)
  
  sf <- 
    merge(sf, rats_description, by=c("RatID"), all.x=TRUE, all.y=TRUE, sort=FALSE) %>% 
    # filter(`Treatment 1` != "ADX") %>%
    pivot_longer(
      cols = c("Left", "Right"),
      names_to = c("Side"),
      values_to = "SF"
    ) %>% 
    mutate(
      SF = SF*(-1),
      Trt = ifelse(replication %in% c(1:6), ifelse(`Treatment 1` == "ADX", "preADX", paste0("pre", Operation)), 
            ifelse(replication %in% c(7:12), ifelse(`Treatment 1` == "ADX", "ADX", Operation),
            ifelse(replication %in% c(13:18), ifelse(`Treatment 1` == "ADX", "ADX+UBI", paste0(Operation, "+Rhiz")), "Pavu"))),
      Day = as.numeric(Day),
      DateD = as.numeric(DateD)
    )
  
  if(count(sf)$n == TEST_ROWS_AFTER_MERGE) print(paste0(TEST_ROWS_AFTER_MERGE, " - ", "OK"))
  
  write_csv(x = sf, PATH_SF_DATA_CSV)
  return(sf)
}


```

```{r input, results='hide'}

myspan <- 0.4
myname0 <- paste0("SF loess(symmetric span=", myspan, ")")

data <- my.rwData()

sf <- 
  data %>%
  filter(Trt != "Pavu") %>%
  rename(MS = Side, repN = replication) %>% 
  select(!`Measuerment method`) %>% 
  mutate(
    RatID = factor(RatID),
    Later = factor(`Operation side` == MS, c(FALSE, TRUE), c("Contra", "Ipsi")),
    OperationSide = factor(`Operation side`, c("Left", "Right"), c("L", "R")),
    MS = factor(MS, c("Left", "Right"), c("L", "R")),
    TrtGroup = factor(Trt),
    Trt = paste0(Trt, ".", OperationSide),
    Trt = factor(Trt),
    repN = factor(as.integer(repN))
  )

# sf[!complete.cases(sf), c("RatID", "Op3", "Trt", "repN", "Later", "SF")] # Any unmatched rats? Any unmeasured forces?
```

The group sizes are (distinct rats only, same rats with different stimulation locations are counted as duplicates)

```{r dataset_n, echo=FALSE}

d.sum <- sf %>% 
  arrange(TrtGroup) %>% 
  group_by(TrtGroup) %>% 
  summarise(rats = length(unique(RatID))) %>%
  pivot_wider(names_from=c(TrtGroup), values_from = rats)

d.sum %>% 
  flextable %>% 
  fontsize(part = "header", size = 9) %>% 
  autofit

```

## SF, 0-2 sec: Visual inspection of smoothing

<!-- Filter 0-2 sec measurements, taking extra 0.5s for better smoothing. -->

```{r SF_combo_dta}

mydta <- sf %>%
  filter(!is.na(SF)) %>%
  droplevels(.) %>%
  mutate(figName = paste0(RatID, ", ", Trt, ", replicate ", repN)) %>%
  select(figName, Later, Time, SF) %>%
  filter(figName == "TBI-250, UBI.R, replicate 12") %>%
  group_by(figName)

```

Stretch force figure combining Contra, Ipsi and their difference.

```{r TBI_250_UBI_R_replicate_12, echo=FALSE, fig.width=12, fig.height=8}

# myspan <- 0.4

name_fig <- "TBI-250, UBI.R, replicate 12"
name_plt <- paste0("raw ", name_fig)

plt[[name_plt]] <- 
  mydta %>%
  filter( figName == name_fig) %>%
  pivot_wider(names_from = Later, values_from = SF) %>%
  mutate( 
    "Contra - Ipsi" = Contra - Ipsi
  ) %>%
  pivot_longer(c("Contra", "Ipsi", "Contra - Ipsi"), names_to = "Limbs", values_to = "SF") %>% 
  ggplot(aes(x = Time, y = SF, group = Limbs, col = Limbs)) + 
  geom_line() + 
  geom_smooth(
    formula = y ~ x, 
    aes(col = paste0("loess ", myspan)), 
    method ="loess", 
    span = myspan, 
    se = FALSE, 
    method.args = list(family="symmetric")
  ) +
  labs(
    title = paste0(myname0, ", ", name_fig), 
    x = "Time (sec)", 
    y = "Stretching force (mg)"
  )

print(plt[[name_plt]])

```

```{r}

doc <- read_pptx()

for(nm in names(plt)) {
  doc <- doc %>%
    add_slide(
      layout = "Title and Content",
      master = "Office Theme"
    ) %>%
    ph_with(
      value = rvg::dml(ggobj = plt[[nm]]),
      location = ph_location_type(
        type = "body"
        #, width=S_width,
        # height=S_height
        ),
      bg = "transparent"
    ) %>%
    ph_with(
      value = nm,
      location = ph_location_type(type = "title")
    )
}

doc %>% print(target = paste0("SF loess(symmetric span0.4)", ".pptx"))

```

Visually check the smoothing by loess(), varying the "span" to see if alternatives are better than our choice. 

```{r check_loess, include=FALSE}

# myspan <- 0.3

junk <- mydta %>%
  group_map( ~{
    theName <- paste(.y)
    ggplot(data=.x, aes(y = SF, x = Time, group = Later, col = Later)) + 
      geom_line() + 
      geom_smooth(formula = y ~ x, aes(col = paste0(myspan + 0.1)), method="loess", span = myspan + 0.1, se=FALSE, method.args=list(family="symmetric")) +
      geom_smooth(formula = y ~ x, aes(col = paste0(myspan - 0.1)), method="loess", span = myspan - 0.1, se=FALSE, method.args=list(family="symmetric")) +
      geom_smooth(formula = y ~ x, aes(col = paste0(myspan)), method="loess", span=myspan, se=FALSE, method.args=list(family="symmetric")) +
      # theme(legend.position = "none") +
      labs(title=paste(myname0, theName), x="Time (sec)", y="Stretching force (mg)")
  } ) %>% 
  setNames(unique(sort(mydta$figName)))

mydta %>% n_groups()

```

```{r write_pptx_check_loess, echo=FALSE, fig.width=12, fig.height=8}

for(nm in unique(mydta$figName)) {
  print(junk[[nm]])
}

# doc <- read_pptx()
# 
# for(nm in unique(mydta$figName)) {
#   doc <- doc %>%
#     add_slide(
#       layout = "Title and Content",
#       master = "Office Theme"
#     ) %>%
#     ph_with(
#       value = rvg::dml(ggobj = junk[[nm]]),
#       location = ph_location_type(
#         type = "body"
#         #, width=S_width,
#         # height=S_height
#         ),
#       bg = "transparent"
#     ) %>%
#     ph_with(
#       value = nm,
#       location = ph_location_type(type = "title")
#     )
# }
# doc %>% print(target = paste0(myname0, "_0.5_.pptx"))

```


<!-- (Heart rate check) -->
<!-- Visually check the smoothing by loess(), varying the "span" to see if alternatives are better than our choice. -->

<!-- ```{r check_loess_heart_rate_check, echo=FALSE, fig.width=12, fig.height=8} -->

<!-- myspan <- 0.05 -->
<!-- junk <- mydta %>% -->
<!--   group_map( ~{ -->
<!--     theName <- paste(.y) -->
<!--     ggplot(data=.x, aes(y = SF, x = Time, group = Later, col = Later)) + -->
<!--       geom_line(size=0.3) + -->
<!--       # geom_smooth(size=0.3, formula = y ~ x, aes(col = paste0(myspan - 0.35)), method="loess", span = myspan - 0.35, se=FALSE, method.args=list(family="symmetric")) + -->
<!--       geom_smooth(size=0.5, formula = y ~ x, aes(col = paste0(myspan)), method="loess", span=myspan, se=FALSE, method.args=list(family="symmetric")) + -->
<!--       # theme(legend.position = "none") + -->
<!--       labs(title=paste(myname0, theName), x="Time (sec)", y="Stretching force (mg)") -->
<!--   } ) %>% -->
<!--   setNames(unique(sort(mydta$figName))) -->



<!-- ``` -->

<!-- ```{r write_pptx_check_loess_heart_rate, echo=FALSE} -->

<!-- doc <- read_pptx() -->

<!-- for(nm in unique(mydta$figName)) { -->
<!--   doc <- doc %>% -->
<!--     add_slide( -->
<!--       layout = "Title and Content", -->
<!--       master = "Office Theme" -->
<!--     ) %>% -->
<!--     ph_with( -->
<!--       value = rvg::dml(ggobj = junk[[nm]]), -->
<!--       location = ph_location_type( -->
<!--         type = "body" -->
<!--         #, width=S_width, -->
<!--         # height=S_height -->
<!--         ), -->
<!--       bg = "transparent" -->
<!--     ) %>% -->
<!--     ph_with( -->
<!--       value = nm, -->
<!--       location = ph_location_type(type = "title") -->
<!--     ) -->
<!-- } -->
<!-- doc %>% print(target = paste0(myname0, "_heart_rate_check.pptx")) -->

<!-- mydta %>% n_groups() -->

<!-- ``` -->


## SF, 0-2 sec: Compute lateralized work (W) and its asymmetry index (AI)

<!-- Define smoother for all Time points. -->

<!-- ```{r smoother_by_Time} -->

<!-- # use as: mutate( Contra_s = smoother_by_Time(., "Contra") ) -->
<!-- smoother_by_Time <- function(dta, y) { -->
<!--   mysm <- loess( -->
<!--     as.formula(paste0(y, "~Time")),  -->
<!--     data = dta,  -->
<!--     family = "symmetric",  -->
<!--     span = myspan -->
<!--     ) -->
<!--   predict(mysm, newdata=dta$Time) # interpolate over NA -->
<!-- } -->

<!-- ``` -->

Define smoother for all Time points.

```{r smoother_W_AI}

# 0-1 0.4-1 1-2 0-2 0.4-2

smoother_W <- function(dta, ...) {

  # dtaF <- dta %>% filter(Time < 10.5, !is.na(SF))

  dtaF <- dta %>% filter(!is.na(SF))

  if(nrow(dtaF) < 1 | ncol(dtaF) < 2) {
    print(dta)
    return(data.frame())
  }

  my.sm <- loess(SF~Time, data=dtaF, family="symmetric", span=myspan)

  i_0_1  <- integrate(function(x) predict(my.sm, newdata=x), 0, 1)
  i_0_4_1  <- integrate(function(x) predict(my.sm, newdata=x), 0.4, 1)
  i_1_2 <- integrate(function(x) predict(my.sm, newdata=x), 1, 2)
  i_0_2 <- integrate(function(x) predict(my.sm, newdata=x), 0, 2)
  i_0_4_2 <- integrate(function(x) predict(my.sm, newdata=x), 0.4, 2)

  data.frame(
    dT = c(
      "T_0_1",
      "T_0.4_1",
      "T_1_2",
      "T_0_2",
      "T_0.4_2"
      ),
    W = c(
      i_0_1$value,
      i_0_4_1$value,
      i_1_2$value,
      i_0_2$value,
      i_0_4_2$value
      )
  )
}

```

Remove unneded columns from SF dataset

```{r clean_SF}

sf_ai_dw <-
  sf %>%
  # filter(RatID == "TBI-250", Trt %in% c("UBI.R")) %>%
  select(Trt, OperationSide, TrtGroup, Operation, RatID, repN, MS, Later, Day, weight, DateD, Time, SF) %>%
  ungroup %>%
  arrange(Trt, OperationSide, Operation, RatID, repN, Later, Time)

```

Compute work (W) as integrals (0-1 sec, 0.4-1 sec, ... ) of smoothed force measurements. dW = W_Contra - W_Ipsi

```{r compute_W_CI}

sf_CI_dW <- sf_ai_dw %>%
  select( -MS ) %>%
  group_by(Trt, OperationSide, TrtGroup, Operation, RatID, repN, Day, weight, DateD) %>%
  pivot_wider(names_from = Later, values_from = SF) %>%
  mutate( SF = Contra - Ipsi ) %>%
  group_modify(smoother_W) %>%
  ungroup %>%
  droplevels(.)

```

Compute AI = log2(Contra/Ipsi) using integrals (0-1 sec, 0.4-1 sec, ...) of smoothed force measurements.

```{r compute_AI_CI}

sf_CI_AI <- sf_ai_dw %>%
  select( -MS ) %>%
  group_by(Trt, OperationSide, TrtGroup, Operation, RatID, repN, Later, Day, weight, DateD) %>%
  group_modify(smoother_W) %>%
  ungroup %>%
  group_by(RatID, Trt, repN, dT) %>%
  pivot_wider(names_from = Later, values_from = W) %>%
  # spread(Later, W) %>%
  mutate( AI = log2( Contra / Ipsi ) ) %>%
  ungroup %>%
  droplevels(.)

```

Compute work (W) as integrals (0-1 sec, 0.4-1 sec, ...) of smoothed force measurements. dW = W_Left - W_Right

```{r compute_W_LR}

sf_LR_dW <- sf_ai_dw %>%
  select( -Later ) %>%
  group_by(Trt, OperationSide, TrtGroup, Operation, RatID, repN, Day, weight, DateD) %>%
  pivot_wider(names_from = MS, values_from = SF) %>%
  # spread(MS, SF) %>%
  mutate( SF = L - R ) %>%
  group_modify(smoother_W) %>%
  ungroup %>%
  droplevels(.)

```

Compute AI = log2(Left/Right) using integrals (0-1 sec, 0.4-1 sec, ...) of smoothed force measurements.

```{r compute_AI_LR}

sf_LR_AI <- sf_ai_dw %>%
  select( -Later ) %>%
  group_by(Trt, OperationSide, TrtGroup, Operation, RatID, repN, MS, Day, weight, DateD) %>%
  group_modify(smoother_W) %>%
  ungroup %>%
  group_by(RatID, Trt, repN, dT) %>%
  pivot_wider(names_from = MS, values_from = W) %>%
  # spread(MS, W) %>%
  mutate( AI = log2( L / R ) ) %>%
  ungroup %>%
  droplevels(.)

```

Save preprocessed SF

```{r smooth}

myname <- paste0("SF Sp 0-1 0.4-1 1-2 0-2 0.4-2 loess(symmetric span", myspan, ")")

# save(sf_CI_dW, sf_CI_AI, sf_LR_dW, sf_LR_AI, sf, file=paste0(myname, "_all_rats_VMaster.RData"))

```

```{r}
load("SF Sp 0-1 0.4-1 1-2 0-2 0.4-2 loess(symmetric span0.4)_all_rats_VMaster.RData")
# rm(sf) # conserve memory, we do not need the raw data

dta_LR_dW <- sf_LR_dW %>%
  filter(dT %in% c("T_0_2")) %>%
  filter(!TrtGroup %in% c("preADX", "ADX", "ADX+UBI")) %>%
  select(!c(Trt, Day, DateD, dT)) %>% 
  droplevels(.)

dta_CI_dW <- sf_CI_dW %>%
  filter(dT %in% c("T_0_2")) %>%
  filter(!TrtGroup %in% c("preADX", "ADX", "ADX+UBI")) %>%
  select(!c(Trt, Day, DateD, dT)) %>% 
  droplevels(.)

dta_LR_AI <- sf_LR_AI %>%
  filter(dT %in% c("T_0_2")) %>%
  filter(!TrtGroup %in% c("preADX", "ADX", "ADX+UBI")) %>%
  select(!c(Trt, Day, DateD, dT, L, R)) %>% 
  droplevels(.)

dta_CI_AI <- sf_CI_AI %>%
  filter(dT %in% c("T_0_2")) %>%
  filter(!TrtGroup %in% c("preADX", "ADX", "ADX+UBI")) %>%
  select(!c(Trt, Day, DateD, dT, Contra, Ipsi)) %>% 
  droplevels(.)
```

```{r}
dta_all.1 <- 
  merge(dta_LR_dW, dta_LR_AI, by=c("OperationSide", "TrtGroup", "Operation", "RatID", "repN", "weight"), all.x=TRUE, all.y=TRUE, sort=FALSE)

dta_all.2 <- 
  merge(dta_CI_dW, dta_CI_AI, by=c("OperationSide", "TrtGroup", "Operation", "RatID", "repN", "weight"), all.x=TRUE, all.y=TRUE, sort=FALSE)

```

```{r}
dta_all <- 
  merge(dta_all.1, dta_all.2, by=c("OperationSide", "TrtGroup", "Operation", "RatID", "repN", "weight"), suffixes = c("_LR","_CI"), all.x=TRUE, all.y=TRUE, sort=FALSE)

dta_all <- 
  dta_all %>% 
  mutate(Time = ifelse(TrtGroup %in% c("preSO", "preUBI"), "Pre", 
                       ifelse(TrtGroup %in% c("SO", "UBI"), "Post", "Rhz")),
         Time = factor(Time, c("Pre", "Post", "Rhz")),
         Operation = ifelse(Operation == "SO", "Sh", Operation),
         Operation = factor(Operation, c("Sh", "UBI")),
         repN = as.numeric(repN)) %>% 
  select(!c(TrtGroup)) %>% 
  relocate(any_of(c("RatID", "Operation", "Time", "OperationSide", "weight", "repN", "W_CI", "AI_CI", "W_LR", "AI_LR")))

write.xlsx(dta_all, "Figure_3_4_Source_data_08d_02_2022.xlsx")

```

```{r}
dta_all %>% 
  arrange(Operation, OperationSide, Time) %>% 
  group_by(Operation, OperationSide, Time) %>% 
  summarise(rats = length(unique(RatID)), .groups = "drop") %>%
  pivot_wider(names_from=c(Time), values_from=rats) %>% 
  flextable %>% autofit
```


```{r}
dta_all_raw <- 
  data %>%
  filter(!Trt %in% c("preADX", "ADX", "ADX+UBI", "Pavu")) %>% 
  mutate(TimeGroup = ifelse(Trt %in% c("preSO", "preUBI"), "Pre", 
                       ifelse(Trt %in% c("SO", "UBI"), "Post", "Rhz")),
         TimeGroup = factor(TimeGroup, c("Pre", "Post", "Rhz")),
         Operation = ifelse(Operation == "SO", "Sh", Operation),
         Operation = factor(Operation, c("Sh", "UBI")),
         OperationSide = ifelse(`Operation side` == "Right", "R", "L"),
         OperationSide = factor(OperationSide, c("R", "L"))) %>% 
  select(c(RatID, Operation, TimeGroup, Time, OperationSide, weight, replication, Side, SF)) %>% 
  pivot_wider(names_from = Side, values_from = SF) %>% 
  ungroup %>% 
  droplevels(.)

write.xlsx(dta_all_raw, "Figure_3_4_Source_data_08d_02_2022_raw_data.xlsx")
  
```


```{r}
dta_all_raw %>% 
  arrange(Operation, OperationSide, TimeGroup) %>% 
  group_by(Operation, OperationSide, TimeGroup) %>% 
  summarise(rats = length(unique(RatID)), .groups = "drop") %>%
  pivot_wider(names_from=c(TimeGroup), values_from=rats) %>% 
  flextable %>% autofit

```



# Integrate square of differences between real measurements and loess approximation 

Define smoother for all Time points.

```{r smoother_V}

# 0-1 0.4-1 1-2 0-2 0.4-2

smoother_V <- function(dta, ...) {

  my.integrate <- function(lower, upper, col) {
    
    sm_loess <- loess(as.formula(paste0(col, "~Time")), data=dta, family="symmetric", span=myspan)
    f_interp <- approxfun(x=dta$Time, y=dta[[col]], method = "linear")
    
    sqrt(integrate(function(x) (predict(sm_loess, newdata=x) - f_interp(x))^2, lower, upper, subdivisions = 10000L, stop.on.error = FALSE)$value)
  }

  i_0_1 <-   my.integrate(0, 1, "Ipsi")
  i_0_4_1 <- my.integrate(0.4, 1, "Ipsi")
  i_0_2 <-   my.integrate(0, 2, "Ipsi")
  i_1_2 <-   my.integrate(1, 2, "Ipsi")
  i_0_4_2 <- my.integrate(0.4, 2, "Ipsi")
  
  i_0_1_c <-   my.integrate(0, 1, "Contra")
  i_0_4_1_c <- my.integrate(0.4, 1, "Contra")
  i_0_2_c <-   my.integrate(0, 2, "Contra")
  i_1_2_c <-   my.integrate(1, 2, "Contra")
  i_0_4_2_c <- my.integrate(0.4, 2, "Contra")

  data.frame(
    dT = c(
      "T_0_1",
      "T_0.4_1",
      "T_0_2",
      "T_1_2",
      "T_0.4_2"
      ),
    V_i = c(
      i_0_1,
      i_0_4_1,
      i_0_2,
      i_1_2,
      i_0_4_2
      ),
    V_c = c(
      i_0_1_c,
      i_0_4_1_c,
      i_0_2_c,
      i_1_2_c,
      i_0_4_2_c
      )
    
  )
}

```

<!-- ```{r} -->
<!-- dtaF <- sf_v %>% -->
<!--   select( -MS ) %>% -->
<!--   group_by(Trt, OperationSide, TrtGroup, Operation, RatID, repN, Day, weight, DateD) %>% -->
<!--   pivot_wider(names_from = Later, values_from = SF) -->

<!-- f_interp <- approxfun(x=dtaF$Time, y=dtaF$Ipsi, method = "linear") -->

<!-- my.sm <- loess(Ipsi~Time, data=dtaF, family="symmetric", span=myspan) -->
<!-- sqrt(cubintegrate(function(x) (predict(my.sm, newdata=x) - f_interp(x))^2, lower = 0, upper = 2)$integral) -->
<!-- # sqrt(integrate(function(x) (predict(my.sm, newdata=x) - f_interp(x))^2, 0, 2, subdivisions = 1000L)$value) -->
<!-- ``` -->

Remove unneded columns from SF dataset

```{r clean_V}

sf_v <-
  sf %>%
  # filter(RatID == "TBI-250", Trt %in% c("UBI.R") & repN == "12") %>%
  select(Trt, OperationSide, TrtGroup, Operation, RatID, repN, MS, Later, Day, weight, DateD, Time, SF) %>%
  ungroup %>%
  arrange(Trt, OperationSide, Operation, RatID, repN, Later, Time)

```

```{r compute_CI_V_I}

sf_CI_V_I <-
  sf_v %>%
  select( -MS ) %>%
  group_by(Trt, OperationSide, TrtGroup, Operation, RatID, repN, Day, weight, DateD) %>%
  pivot_wider(names_from = Later, values_from = SF) %>%
  # mutate( SF = Contra - Ipsi ) %>%
  group_modify(smoother_V) %>%
  ungroup %>%
  droplevels(.)
```

Save Variances

```{r smooth_v}

myname <- paste0("SF 0-1 0.4-1 1-2 0-2 0.4-2 loess(symmetric span", myspan, ")")

# save(sf_CI_V_I,  file=paste0(myname, "_Variances.RData"))

```