---
title: "Vertical Analysis MPA: Ctrl, Saline (L, R; hand, machine)"
author: "Yaromir Kobikov <kobikov.yaromir@gmail.com>"
date: "Date: `r format(Sys.time(), '%d/%m/%Y')`"
output:
  word_document: default
  html_document:
    toc: true
    toc_float:
      collapsed: false
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
source("../BayesianPValue.R")
```

# MPA (Magnitude of Postural asymmetry)

Values in “+”.

# Read Data

Read from Excel file.

```{r input}

file_name <- "data/SDU-RDPA-Stat_v2.xlsx"
sheet <- "SDU-RD-Stat-v2"

my.seed <- 20231201 # reproducible Bayessian fit

myname0 <- "MPA"

main_dir <- "../" # path to the base folder, containing data and results
path_rds <- "rds/vertical_analysis/mpa_negbinomial/" # folder to store the results 
DESIGN <- "RD" # only reverse design data will be used
full_rds_path = paste0(main_dir, path_rds)

dir.create(file.path(main_dir, path_rds), showWarnings = FALSE)

data <-
  file.path(main_dir, file_name) %>% 
  read_excel(sheet, .name_repair = "universal", na = c("", "NA", "NULL")) %>%
  mutate(
    RatID = Rat.ID,
    Side = recode_factor(Operation.side, Left='L', Right='R'),
    Dose = factor(Anesthesia.dosage..route, c("40 mg/kg, i.p.", "60 mg/kg, i.p."), c("40", "60")),
    Treatment.4 = factor(...13),
    WPre = BW.1,
    WPost = BW.2,
    Group3 = ifelse(is.na(Treatment.1), "Ctrl", Treatment.1)
    # Trt4 = ifelse(is.na(Treatment.1) & (!is.na(Treatment.3) & (Treatment.3 != 'Saline')), "Ctrl", Treatment.3)
  ) %>% 
  select(
    RatID, Date, Side, Measurement.method, Dose, Treatment.1, Treatment.3, Treatment.4, WPre, WPost, Group3,
    starts_with(c("PA1.", "PA2.", "PA3.", "PA4.", "PA5.", "PA6."))
  ) %>% 
  pivot_longer(
    cols = PA1.1:PA6.6,
    names_to = c("Time"),
    names_pattern = "PA(.)",
    values_to = "PA"
  ) %>% 
  mutate(
    RatID = factor(RatID),
    Time = factor(Time, c("1", "2", "3", "4", "5", "6"), c("0h", "3h", "3h20m", "4h", "4h20m", "5h")),
    Group4 = ifelse(Group3 == 'Ctrl' & Time == '3h' & (!is.na(Treatment.3) & (Treatment.3 != 'Saline')), 'Ctrl', Treatment.3),
    Group4.Side = ifelse(Group4 != 'Ctrl', paste0(Side, '.', Group4), Group4),
    Group4 = factor(Group4, c("Ctrl", "Saline", "NTI", "Nal")),
    Group4.Side = factor(Group4.Side, c("Ctrl", "L.Saline", "R.Saline", "L.NTI", "R.NTI", "L.Nal", "R.Nal")),
    MPA = abs(PA),
    MPA.int = MPA / 0.5
  ) %>%
  drop_na("PA") %>%
  ungroup %>% droplevels(.)

data_hand <-
  data %>%
  filter(Measurement.method == "Hand") %>% 
  droplevels(.)

data_machine <-
  data %>%
  filter(Measurement.method == "MP") %>% 
  droplevels(.)

```
# Ctrl vs Saline (L, R):
In the control group, only those rats that were not injected with anything and with asymmetry > 1.5 mm.

The group sizes are (distinct rats only, same rats with different stimulation locations are counted as duplicates)

```{r input2, echo=FALSE}

data.ctrl.saline_hand <- data_hand %>% 
  filter((Time == '3h' & Group4 == 'Ctrl' | Time == '4h'), !is.na(Group4)) %>% 
  droplevels(.)
data.ctrl.saline_machine <- data_machine %>% 
  filter((Time == '3h' & Group4 == 'Ctrl' | Time == '4h'), !is.na(Group4)) %>% 
  droplevels(.)

data.saline_hand <- data_hand %>% 
  filter(Group4 == 'Saline', Time %in% c("3h", "4h")) %>% 
  droplevels(.)
data.saline_machine <- data_machine %>% 
  filter(Group4 == 'Saline', Time %in% c("3h", "4h")) %>% 
  droplevels(.)


data.ctrl.saline_hand %>% 
  arrange(Group4.Side, Time) %>% 
  group_by(Group4.Side, Time) %>% 
  summarise(rats = length(unique(RatID)), .groups = "drop") %>%
  select(!Time) %>%
  # pivot_wider(names_from=c(Time), values_from=rats) %>%
  # replace_na(list("3h"=0, "4h"=0)) %>%
  flextable %>% autofit

```


```{r}
d1 <-
  data.ctrl.saline_machine %>%
  filter(Group4.Side %in% c("Ctrl", "L.Saline", "R.Saline")) %>%
  droplevels(.)

get_prior(
  data = d1,
  family = negbinomial,
  MPA.int ~ 0 + Group4.Side + (1|RatID)
)
```


# (Hand) Analyse Ctrl and Saline: Ctrl(3h) vs L-Saline(4h) vs R-Saline(4h) injection

If "L,R Saline" is not significantly different from "Ctrl" (by MPA) groups we can merge them into single "Ctrl" group to test against with other injections.

## MPA: Student Model

Prior predictive check

```{r hand_ctrl_mpa_check_prior}

d1 <- 
  data.ctrl.saline_hand %>%
  filter(Group4.Side %in% c("Ctrl", "L.Saline", "R.Saline")) %>% 
  droplevels(.)

myname <- paste0(myname0, "_Ctrl_Hand")

std.prior <- brm(
  data = d1,
  family = hurdle_poisson,
  MPA.int ~ 0 + Group4.Side + (1|RatID),
  # prior = c(prior(student_t(3, 0, 2.5), class = "sd"),
  #           prior(normal(0.1, 1), class = "b")),
  seed = my.seed, 
  chains = my.cores, 
  cores = my.cores, 
  iter = 4e4,
  # sample_prior = "only",
  file = paste0(full_rds_path, "ctrl_check_priornormal53only.rds"),
  file_refit = "on_change"
)

cond_eff <- conditional_effects(std.prior, 
                                "Group4.Side", 
                                method="fitted")
                                #conditions=make_conditions(d1, vars = c("Time")))

plt[["Ctrl MPA prior vs data (hand)"]] <- plot(cond_eff, 
                                       points = TRUE, 
                                       point_args = list(width = 0.1, shape="o", col="red"),
                                       plot=FALSE)[[1]] + 
                                  geom_hline(yintercept=0, linetype="dashed", color="black")

set.seed(2)
plt[["Ctrl MPA prior pp_check (hand)"]] <- pp_check(std.prior, ndraws = 11)

print(cond_eff[[1]])
print(plt[["Ctrl MPA prior vs data (hand)"]])
print(plt[["Ctrl MPA prior pp_check (hand)"]])

```

Model fit and QC:

```{r hand_ctrl_mpa_model_summary, echo=FALSE, fig.width = 10}

std.fit <-  update(std.prior, 
                   sample_prior = "yes",
                   # control = list(adapt_delta = 0.99),
                   seed = my.seed, 
                   cores = my.cores,
                   file = paste0(full_rds_path, "ctrl_model_summary1.rds"),
                   file_refit = "on_change")
summary(std.fit)

```

## MPA: MCMC conversion diagnostics

Posterior predictive check

```{r hand_ctrl_mpa_MCMC_ppcheck}

set.seed(2) # reproducible pp_check

plt[["Ctrl MPA pp_check (hand)"]] <- pp_check(std.fit, ndraws = 21)

print(plt[["Ctrl MPA pp_check (hand)"]])

```

Autocorrelations

```{r hand_ctrl_mpa_MCMC_ac}

plt[["Ctrl MPA ac (hand)"]] <- stan_ac(std.fit$fit)

print(plt[["Ctrl MPA ac (hand)"]])

```

## MPA: Estimated model marginals

Estimated model medians +- 95% HPDCI (HPDCI = highest posterior density continuous interval) as a table:

```{r hand_ctrl_mpa_emm}

emm <- emmeans(std.fit, ~ Group4.Side, regrid = "response", nesting = NULL)
emm_show(emm)

```

Estimated model means as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_ctrl_mpa_emm_plot, echo=FALSE, fig.width = 8}

plt[["Ctrl MPA emm (hand)"]] <- emm %>% emm_inorder %>%
  ggplot(aes(y = fct_rev(interaction(Group4.Side, sep=", ", drop=TRUE)), x = .value, fill = Group4.Side)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  # geom_vline(xintercept=threshold, linetype="dashed", color="black") +
  # geom_vline(xintercept=-threshold, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA (mm) Ctrl and Saline")

print(plt[["Ctrl MPA emm (hand)"]])

```

<!-- Estimated model means as a median +- 95% HPDCI ("x" - mean values of measurements for each rat) -->

<!-- ```{r points_hand_ctrl_mpa_emm_plot, echo=FALSE, fig.width=8} -->

<!-- plt[["Ctrl MPA emm (hand) with Data Points"]] <-  -->
<!--   plt[["Ctrl MPA emm (hand)"]] + -->
<!--     geom_point( -->
<!--       pch = 4, -->
<!--       position = position_nudge(y=0.15), -->
<!--       data = { -->
<!--         d1 %>% -->
<!--           group_by(RatID, Group4.Side) %>% -->
<!--           summarise(.value = mean(MPA), .groups = "drop") -->
<!--       }, -->
<!--       aes(x=.value)) -->

<!-- print(plt[["Ctrl MPA emm (hand) with Data Points"]]) -->

<!-- ``` -->

## MPA: Contrasts

Contrasts BI vs SS as a table:

```{r hand_ctrl_mpa_contrasts}

emmc <- contrast(emm, simple = "Group4.Side", method = "trt.vs.ctrl1")
emm_show(emmc)

```

Contrasts BI vs SS as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_ctrl_mpa_plot, echo=FALSE, fig.width = 8}

plt[["Ctrl MPA by Side (hand)"]] <- emmc %>% emm_inorder %>%
  ggplot(aes( y = fct_rev(interaction(contrast, sep=", ", drop=TRUE)), x=.value, fill=contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA in mm, contrast: Ctrl vs L,R-Saline")

print(plt[["Ctrl MPA by Side (hand)"]])

```

# v2 (Hand) Analyse Ctrl and Saline: Ctrl(3h) vs L-Saline(4h) vs R-Saline(4h) injection

If "L,R Saline" is not significantly different from "Ctrl" (by MPA) groups we can merge them into single "Ctrl" group to test against with other injections.

## MPA: Student Model

Prior predictive check

```{r v2hand_ctrl_mpa_check_prior}

d1 <- 
  data.ctrl.saline_hand %>%
  filter(Group4.Side %in% c("Ctrl", "L.Saline", "R.Saline")) %>% 
  droplevels(.)

myname <- paste0(myname0, "_Ctrl_Hand")

std.prior <- brm(
  data = d1,
  family = negbinomial,
  MPA.int ~ 0 + Group4.Side + (1|RatID),
  prior = # c(prior(student_t(3, 0, 10), class = "sd"),
            prior(normal(0, 1.5), class = "b"),
  seed = my.seed, 
  chains = my.cores, 
  cores = my.cores, 
  iter = 4e4,
  sample_prior = "only",
  file = paste0(full_rds_path, "ctrl_check_priorv2.303010.rds"),
  file_refit = "on_change"
)

cond_eff <- conditional_effects(std.prior, 
                                "Group4.Side", 
                                method="fitted")
                                #conditions=make_conditions(d1, vars = c("Time")))

plt[["Ctrl MPA prior vs data (hand)"]] <- plot(cond_eff, 
                                       points = TRUE, 
                                       point_args = list(width = 0.1, shape="o", col="red"),
                                       plot=FALSE)[[1]] + 
                                  geom_hline(yintercept=0, linetype="dashed", color="black")

set.seed(2)
plt[["Ctrl MPA prior pp_check (hand)"]] <- pp_check(std.prior, ndraws = 11)

print(cond_eff[[1]])
print(plt[["Ctrl MPA prior vs data (hand)"]])
print(plt[["Ctrl MPA prior pp_check (hand)"]])

```

Model fit and QC:

```{r v2hand_ctrl_mpa_model_summary, echo=FALSE, fig.width = 10}

std.fit <-  update(std.prior, 
                   sample_prior = "yes",
                   # control = list(adapt_delta = 0.99),
                   seed = my.seed, 
                   cores = my.cores,
                   file = paste0(full_rds_path, "ctrl_model_summaryv2.normal0075.rds"),
                   file_refit = "on_change")
summary(std.fit)

```

## MPA: MCMC conversion diagnostics

Posterior predictive check

```{r v2hand_ctrl_mpa_MCMC_ppcheck}

set.seed(2) # reproducible pp_check

plt[["Ctrl MPA pp_check (hand)"]] <- pp_check(std.fit, ndraws = 21)

print(plt[["Ctrl MPA pp_check (hand)"]])

```

Autocorrelations

```{r v2hand_ctrl_mpa_MCMC_ac}

plt[["Ctrl MPA ac (hand)"]] <- stan_ac(std.fit$fit)

print(plt[["Ctrl MPA ac (hand)"]])

```

## MPA: Estimated model marginals

Estimated model medians +- 95% HPDCI (HPDCI = highest posterior density continuous interval) as a table:

```{r v2hand_ctrl_mpa_emm}

emm <- emmeans(std.fit, ~ Group4.Side, regrid = "response", nesting = NULL)
emm_show(emm)

```

Estimated model means as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r v2hand_ctrl_mpa_emm_plot, echo=FALSE, fig.width = 8}

plt[["Ctrl MPA emm (hand)"]] <- emm %>% emm_inorder %>%
  ggplot(aes(y = fct_rev(interaction(Group4.Side, sep=", ", drop=TRUE)), x = .value, fill = Group4.Side)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  # geom_vline(xintercept=threshold, linetype="dashed", color="black") +
  # geom_vline(xintercept=-threshold, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA (mm) Ctrl and Saline")

print(plt[["Ctrl MPA emm (hand)"]])

```

<!-- Estimated model means as a median +- 95% HPDCI ("x" - mean values of measurements for each rat) -->

<!-- ```{r points_hand_ctrl_mpa_emm_plot, echo=FALSE, fig.width=8} -->

<!-- plt[["Ctrl MPA emm (hand) with Data Points"]] <-  -->
<!--   plt[["Ctrl MPA emm (hand)"]] + -->
<!--     geom_point( -->
<!--       pch = 4, -->
<!--       position = position_nudge(y=0.15), -->
<!--       data = { -->
<!--         d1 %>% -->
<!--           group_by(RatID, Group4.Side) %>% -->
<!--           summarise(.value = mean(MPA), .groups = "drop") -->
<!--       }, -->
<!--       aes(x=.value)) -->

<!-- print(plt[["Ctrl MPA emm (hand) with Data Points"]]) -->

<!-- ``` -->

## MPA: Contrasts

Contrasts BI vs SS as a table:

```{r v2hand_ctrl_mpa_contrasts}

emmc <- contrast(emm, simple = "Group4.Side", method = "trt.vs.ctrl1")
emm_show(emmc)

```

Contrasts BI vs SS as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r v2hand_ctrl_mpa_plot, echo=FALSE, fig.width = 8}

plt[["Ctrl MPA by Side (hand)"]] <- emmc %>% emm_inorder %>%
  ggplot(aes( y = fct_rev(interaction(contrast, sep=", ", drop=TRUE)), x=.value, fill=contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA in mm, contrast: Ctrl vs L,R-Saline")

print(plt[["Ctrl MPA by Side (hand)"]])

```

# Poisson (Hand) Analyse Ctrl and Saline: Ctrl(3h) vs L-Saline(4h) vs R-Saline(4h) injection

If "L,R Saline" is not significantly different from "Ctrl" (by MPA) groups we can merge them into single "Ctrl" group to test against with other injections.

## MPA: Student Model

Prior predictive check

```{r v3hand_ctrl_mpa_check_prior}

d1 <- 
  data.ctrl.saline_hand %>%
  filter(Group4.Side %in% c("Ctrl", "L.Saline", "R.Saline")) %>% 
  droplevels(.)

myname <- paste0(myname0, "_Ctrl_Hand")

std.prior <- brm(
  data = d1,
  family = poisson,
  MPA.int ~ 0 + Group4.Side + (1|RatID),
  # prior = prior(normal(0, 1), class = "b"),
  seed = my.seed, 
  chains = my.cores, 
  cores = my.cores, 
  iter = 4e4,
  # sample_prior = "only",
  file = paste0(full_rds_path, "ctrl_check_prior.poisson.rds"),
  file_refit = "on_change"
)

cond_eff <- conditional_effects(std.prior, 
                                "Group4.Side", 
                                method="fitted")
                                #conditions=make_conditions(d1, vars = c("Time")))

plt[["Ctrl MPA prior vs data (hand)"]] <- plot(cond_eff, 
                                       points = TRUE, 
                                       point_args = list(width = 0.1, shape="o", col="red"),
                                       plot=FALSE)[[1]] + 
                                  geom_hline(yintercept=0, linetype="dashed", color="black")

set.seed(2)
plt[["Ctrl MPA prior pp_check (hand)"]] <- pp_check(std.prior, ndraws = 11)

print(cond_eff[[1]])
print(plt[["Ctrl MPA prior vs data (hand)"]])
print(plt[["Ctrl MPA prior pp_check (hand)"]])

```

Model fit and QC:

```{r v3hand_ctrl_mpa_model_summary, echo=FALSE, fig.width = 10}

std.fit <-  update(std.prior, 
                   sample_prior = "yes",
                   # control = list(adapt_delta = 0.99),
                   seed = my.seed, 
                   cores = my.cores,
                   file = paste0(full_rds_path, "ctrl_model_summary.poisson.rds"),
                   file_refit = "on_change")
summary(std.fit)

```

## MPA: MCMC conversion diagnostics

Posterior predictive check

```{r v3hand_ctrl_mpa_MCMC_ppcheck}

set.seed(2) # reproducible pp_check

plt[["Ctrl MPA pp_check (hand)"]] <- pp_check(std.fit, ndraws = 21)

print(plt[["Ctrl MPA pp_check (hand)"]])

```

Autocorrelations

```{r v3hand_ctrl_mpa_MCMC_ac}

plt[["Ctrl MPA ac (hand)"]] <- stan_ac(std.fit$fit)

print(plt[["Ctrl MPA ac (hand)"]])

```

## MPA: Estimated model marginals

Estimated model medians +- 95% HPDCI (HPDCI = highest posterior density continuous interval) as a table:

```{r v3hand_ctrl_mpa_emm}

emm <- emmeans(std.fit, ~ Group4.Side, regrid = "response", nesting = NULL)
emm_show(emm)

```

Estimated model means as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r v3hand_ctrl_mpa_emm_plot, echo=FALSE, fig.width = 8}

plt[["Ctrl MPA emm (hand)"]] <- emm %>% emm_inorder %>%
  ggplot(aes(y = fct_rev(interaction(Group4.Side, sep=", ", drop=TRUE)), x = .value, fill = Group4.Side)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  # geom_vline(xintercept=threshold, linetype="dashed", color="black") +
  # geom_vline(xintercept=-threshold, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA (mm) Ctrl and Saline")

print(plt[["Ctrl MPA emm (hand)"]])

```

<!-- Estimated model means as a median +- 95% HPDCI ("x" - mean values of measurements for each rat) -->

<!-- ```{r points_hand_ctrl_mpa_emm_plot, echo=FALSE, fig.width=8} -->

<!-- plt[["Ctrl MPA emm (hand) with Data Points"]] <-  -->
<!--   plt[["Ctrl MPA emm (hand)"]] + -->
<!--     geom_point( -->
<!--       pch = 4, -->
<!--       position = position_nudge(y=0.15), -->
<!--       data = { -->
<!--         d1 %>% -->
<!--           group_by(RatID, Group4.Side) %>% -->
<!--           summarise(.value = mean(MPA), .groups = "drop") -->
<!--       }, -->
<!--       aes(x=.value)) -->

<!-- print(plt[["Ctrl MPA emm (hand) with Data Points"]]) -->

<!-- ``` -->

## MPA: Contrasts

Contrasts BI vs SS as a table:

```{r v3hand_ctrl_mpa_contrasts}

emmc <- contrast(emm, simple = "Group4.Side", method = "trt.vs.ctrl1")
emm_show(emmc)

```

Contrasts BI vs SS as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r v3hand_ctrl_mpa_plot, echo=FALSE, fig.width = 8}

plt[["Ctrl MPA by Side (hand)"]] <- emmc %>% emm_inorder %>%
  ggplot(aes( y = fct_rev(interaction(contrast, sep=", ", drop=TRUE)), x=.value, fill=contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA in mm, contrast: Ctrl vs L,R-Saline")

print(plt[["Ctrl MPA by Side (hand)"]])

```

