---
title: "SF, CI AI (Ctrl, NTI, Nal): Bayesian regression of smoothed stretch forces"
author: "Yaromir Kobikov <kobikov.yaromir@gmail.com>"
date: "Date: `r format(Sys.time(), '%d/%m/%Y')`"
output:
  word_document: default
  html_document:
    toc: true
    toc_float:
      collapsed: false
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}

source("../../BayesianPValue.R")

```

 # Read SF data 

# LEFT VS RIGHT but not contra vs ipsi

The resistance was measured as the amount of mechanical work $W_{contra}$ and $W_{ipsi}$ to stretch the contra- and ipsilesional hindlimbs, where $W(T_{0-2}) = \int_{t=0}^{2} f(t)$ was stretching  force integrated over stretching distance interval from 0 to 10 mm. Asymmetry was assessed as the contra-/ipsilesional asymmetry index $AI_W = log2(W_{contra} / W_{ipsi})$. The control intact rat showed symmetric $W$ pattern; the $W$ for the left and right limbs were calculated instead of $W_{contra}$ and $W_{ipsi}$ for this animal.

```{r input}

my.seed <- 20231103 # reproducible Bayessian fit
my.span <- 0.4

# rds_folder_name <- "../../rds/sf/ctrl_nti_nal/sf_0-2_LR_AI/"
rds_folder_name <- "../../rds/sf/ctrl_nti_nal/sf_0-2_CI_AI/"

dir.create(file.path(rds_folder_name), showWarnings = FALSE)

load("../SF Sp 0-1 0.4-1 1-2 0-2 0.4-2 loess(symmetric span0.4)_Ctrl_NTI_Nal.RData")
rm(sf) # conserve memory, we do not need the raw data


# dta <- sf_LR_AI %>%
dta <- sf_CI_AI %>%
  filter(dT %in% c("T_0_2")) %>%
  rename(Op3 = Group3, Time = Period) %>% 
  mutate(WPost_scaled = scale(WPost)) %>% 
  droplevels(.)

```

The median (bars) and 95% HPDCI (whiskers) for SF AI data points. __NOT__ the uncertainties estimated by Bayesian model. By time.

```{r plot_bars_hpdci_time}

myname <- "SF 0-2 span=0.4 [Ctrl, NTI-[L,R], Nal-[L,R]]"

plt[["Ctrl, NTI-[L,R], Nal-[L,R] time"]] <- 
  dta %>% 
  group_by(Op3, Time) %>% 
  median_hdci(AI, .width = 0.95) %>%
  ungroup() %>%
  ggplot(aes(x=interaction(Time, sep=", ", drop=TRUE), y=AI, fill=Op3)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=.lower, ymax=.upper),
                  width=.2,   # Width of the error bars
                  position=position_dodge(.9)) +
    geom_hline(yintercept=0, linetype="dashed", color="black") +
    theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
    labs(title=myname, x="Medians and 95% HDCI", y="AI")

print(plt[["Ctrl, NTI-[L,R], Nal-[L,R] time"]])

```
The group sizes are (distinct rats only, same rats with different stimulation locations are counted as duplicates)

```{r input2_lr_time, echo=FALSE}

d.sum <- dta %>% 
  arrange(Op3, OperationSide, Time) %>% 
  group_by(Op3, OperationSide, Time) %>% 
  summarise(rats = length(unique(RatID)) ) %>%
  pivot_wider(names_from=c(Time), values_from=rats)

d.sum %>% flextable %>% autofit

```

The median (bars) and 95% HPDCI (whiskers) for SF AI data points. __NOT__ the uncertainties estimated by Bayesian model.

```{r plot_bars_hpdci_lr}

myname <- "SF 0-2 span=0.4 [Ctrl, NTI-[L,R], Nal-[L,R]]"

plt[["Ctrl, NTI-[L,R], Nal-[L,R]"]] <- 
  dta %>% 
  group_by(Op3) %>% 
  median_hdci(AI, .width = 0.95) %>%
  ungroup() %>%
  ggplot(aes(x="", y=AI, fill=Op3)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=.lower, ymax=.upper),
                  width=.2,   # Width of the error bars
                  position=position_dodge(.9)) +
    geom_hline(yintercept=0, linetype="dashed", color="black") +
    theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
    labs(title=myname, x="Medians and 95% HDCI", y="AI")

print(plt[["Ctrl, NTI-[L,R], Nal-[L,R]"]])

```

The group sizes are (distinct rats only, same rats with different stimulation locations are counted as duplicates)

```{r input2, echo=FALSE}

d.sum <- dta %>% 
  arrange(Op3) %>% 
  group_by(Op3) %>% 
  summarise(rats = length(unique(RatID)) ) %>%
  pivot_wider(names_from=c(Op3), values_from=rats)

d.sum %>% flextable %>% autofit

```

# Analyse Ctrl (3h + Saline(4h)) vs NTI [L=8, R=8], Naloxone [L=7, R=7]

## SF AI: Bayesian regression, student family

Prior predictive check

```{r get_prior_lr, include=FALSE}

get_prior(data = dta,
  family = gaussian,
  AI ~ 0 + Op3 + repN + (1|RatID))

```


```{r sf_check_prior_pre}

std.prior <- brm(
  data = dta,
  # family = student,
  family = gaussian,
  # AI ~ 0 + Op3 + WPost + repN + (1|RatID),
  
  AI ~ 0 + Op3*WPost_scaled + (1|RatID),
  
  # AI ~ 0 + Op3 + repN + (1|RatID),
  prior = c(prior(normal(0, 3), class = "sigma"),
            prior(normal(0, 3), class = "sd"),
            prior(normal(0, 5), class = "b")),
  # prior = c(prior(student_t(3, 0, 10), class = "sigma"),
  #         prior(student_t(3, 0, 10), class = "sd"),
  #         prior(normal(0, 5), class = "b")),
  seed = my.seed, 
  chains = my.cores, 
  cores = my.cores, 
  iter = 4e4,
  sample_prior = "only",
  file = paste0(rds_folder_name, "ctrl_nti_nal_check_prior_WPost_scaled_2023_04_05.rds"),
  file_refit = "on_change"
)


cond_eff <- conditional_effects(std.prior,
                                "Op3",
                                method="fitted"
                                # conditions=make_conditions(dta, vars = c("Time"))
                                )

plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] prior check"]] <- plot(cond_eff,
                                       points = TRUE,
                                       point_args = list(width = 0.1, shape="o", col="red"),
                                       plot=FALSE)[[1]] +
                                  geom_hline(yintercept=0, linetype="dashed", color="black")

set.seed(2)
plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] prior pp_check"]] <- pp_check(std.prior, ndraws = 11)

print(cond_eff[[1]])
print(plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] prior check"]])
print(plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] prior pp_check"]])

```

Model fit and QC:

```{r sf_model_summary_pre, echo=FALSE, fig.width = 10}

std.fit <-  update(std.prior, 
                   sample_prior = "yes",
                   # control = list(adapt_delta = 0.99),
                   # control = list(max_treedepth = 15),
                   seed = my.seed, 
                   cores = my.cores,
                   file = paste0(rds_folder_name, "ctrl_nti_nal_model_summary_WPost_scaled_2023_04_05.rds"),
                   file_refit = "on_change")
summary(std.fit)

print(plot(conditional_effects(std.fit), ask=FALSE, plot=FALSE))

```

## SF AI: MCMC conversion diagnostics

Posterior predictive check

```{r sf_MCMC_ppcheck_pre}

set.seed(2) # reproducible pp_check

plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] pp_check"]] <- pp_check(std.fit, ndraws = 21)

print(plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] pp_check"]])

```

Autocorrelations

```{r sf_MCMC_ac_pre}

plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] ac"]] <- stan_ac(std.fit$fit)

print(plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] ac"]])

```

## SF AI: Estimated model marginals

Estimated model medians +- 95% HPDCI (HPDCI = highest posterior density continuous interval) as a table:

```{r sf_emm_pre}

emm <- emmeans(std.fit, ~ Op3*WPost_scaled, regrid = "response", nesting=NULL)
emm_show(emm)

```

Estimated model means as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r sf_emm2_pre, echo=FALSE, fig.width = 8}

plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] emm"]] <- emm %>% emm_inorder %>%
  ggplot(aes(x = Op3, y = .value, fill = Op3)) %>%
  my.stat_eye() +
  geom_hline(yintercept=0, linetype="dashed", color="black") +
  labs(title=myname, x="Estimated Marginal Medians and 95% HPDCI", y="AI")

print(plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] emm"]])

```

```{r points_sf_emm2_pre, echo=FALSE, fig.width=8}

plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] emm with Data Points"]] <- 
  plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] emm"]] +
    geom_point(
      pch = 4,
      position = position_jitterdodge(jitter.width = 0.9, jitter.height = 0, dodge.width = 0.9, seed = 2),
      data = {
        dta %>%
          # group_by(RatID, Op3, OperationSide) %>%
          group_by(RatID, Op3) %>%
          summarise(.value = mean(AI), .groups = "drop")
      },
      # aes(y=.value, color=OperationSide))
      aes(y=.value))

print(plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] emm with Data Points"]])

```

```{r}
dta_without.Ctrl <- dta %>% 
  # filter(Op3 != 'Ctrl') %>% 
  # droplevels(.) %>% 
  mutate(WPost_scaled=scale(WPost))

std.fit = brm(
  AI ~ 0 + Op3*WPost_scaled + (1|RatID), 
  data = dta_without.Ctrl ,
  control = list(max_treedepth = 12),
  iter=1e4,
  file_refit = "on_change",
  file =paste0(rds_folder_name, "ctrl_nti_nal_check_prior_wpost_TEST_without_ctrl_CI_AI.rds")
)
```

```{r}
summary(std.fit)
```

```{r}
dta_without.Ctrl %>%
  group_by(Op3) %>%
  data_grid(WPost_scaled = seq_range(WPost_scaled, n = 101)) %>%
  add_predicted_draws(std.fit, re_formula = NA) %>%
  ggplot(aes(x = WPost_scaled, y = AI, color = Op3, fill = Op3)) +
  stat_lineribbon(aes(y = .prediction), .width = c(.95, .80, .50), alpha = 1/4) +
  geom_point(
      pch = ifelse(dta_without.Ctrl$OperationSide == 'L', 1, 4),
      data = dta_without.Ctrl,
      aes(y=AI)
  ) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Dark2") +
  facet_grid(. ~ Op3, space = "free_x", scales = "free_x")
```


<!-- ```{r} -->
<!-- dta %>% -->
<!--   group_by(RatID, Op3, OperationSide, WPost) %>% -->
<!--   summarise(.value = mean(AI), .groups = "drop") %>%  -->
<!--   ggplot(aes(x=Op3, y=WPost, color=OperationSide)) + -->
<!--   geom_point( -->
<!--     pch = 4, -->
<!--     position = position_jitterdodge(jitter.width = 0.5, jitter.height = 0, dodge.width = 0.5, seed = 2)) -->
<!-- ``` -->


<!-- ```{r} -->
<!-- plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] emm with Data Points"]] <-  -->
<!--   plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] emm"]] + -->
<!--     geom_point( -->
<!--       pch = 4, -->
<!--       position = position_jitterdodge(jitter.width = 0.9, jitter.height = 0, dodge.width = 0.9, seed = 2), -->
<!--       data = { -->
<!--         dta %>% -->
<!--           group_by(RatID, Op3, OperationSide, WPost) %>% -->
<!--           summarise(.value = mean(AI), .groups = "drop") -->
<!--       }, -->
<!--       aes(y=.value, color=OperationSide)) -->

<!-- print(plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] emm with Data Points"]]) -->
<!-- ``` -->

The bar and whiskers plot:

```{r sf_bar_whiskers_pre, echo=FALSE}

plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] bar whiskers"]] <- emm %>% gather_emmeans_draws %>% 
  median_hdci(.width = 0.95) %>% 
  ungroup() %>%
  ggplot(aes(x = interaction(Op3, sep=", ", drop=TRUE), y = .value, fill = Op3)) + 
    geom_bar(position=position_dodge(), aes(y=.value),stat="identity") +
    geom_errorbar(aes(ymin=.lower, ymax=.upper),
                  width=.2,   # Width of the error bars
                  position=position_dodge(.9)) +
    geom_hline(yintercept=0, linetype="dashed", color="black") +
    theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
    labs(title=myname, x="Medians and 95% HDCI", y="AI")

print(plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] bar whiskers"]])

```

The ccdinterval plot with same data as above bars and whiskers:

```{r sf_ccdfinterval_pre, echo=FALSE}

plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] ccdfinterval"]] <- emm %>% gather_emmeans_draws %>%
  ggplot(aes(x = interaction(Op3, sep=", ", drop=TRUE), y = .value, fill = Op3)) +
  stat_ccdfinterval(point_interval = median_hdci, .width = 0.95,
             shape = 16, point_color = "black", interval_color = "black", 
             position="dodge", slab_color = NA) +
    scale_fill_brewer(palette = "Set2") + 
    scale_color_brewer(palette = "Dark2") +
    theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  # coord_cartesian(ylim = c(0, 15.5), expand=FALSE) +
  geom_hline(yintercept=0, linetype="dashed", color="black") +
  labs(title=myname, x="Estimated Marginal Medians and 95% HPDCI", y="AI")

print(plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] ccdfinterval"]])

```

```{r points_sf_ccdfinterval_pre, echo=FALSE, fig.width=8}

plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] ccdfinterval with Data Points"]] <- 
  plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] ccdfinterval"]] +
    geom_point(
      pch = 4,
      position = position_jitterdodge(jitter.width = 0.9, jitter.height = 0, dodge.width = 0.9, seed = 2),
      data = {
        dta %>%
          group_by(RatID, Op3) %>%
          summarise(.value = mean(AI), .groups = "drop")
      },
      aes(y=.value))

print(plt[["SF Ctrl, NTI-[L,R], Nal-[L,R] ccdfinterval with Data Points"]])

```

## SF AI: Contrasts

Contrasts Ctrl, NTI-[L,R], Nal-[L,R] as a table:

```{r sf_contrasts}

emmc <- contrast(emm, simple = "Op3", method = "trt.vs.ctrl1")
emm_show(emmc)

```

Contrasts Ctrl, NTI-[L,R], Nal-[L,R] as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval).

```{r sf_by_contrasts, echo=FALSE, fig.width = 8}

plt[["SF contrast Ctrl, NTI-[L,R], Nal-[L,R]"]] <- emmc %>% emm_inorder %>% 
  ggplot(aes(x = interaction(contrast, sep=", ", drop=TRUE), y = .value, fill = contrast)) %>%
  my.stat_eye() +
  geom_hline(yintercept=0, linetype="dashed", color="black") +
  labs(title=myname, x="0-2 sec", y="AI, between groups and ctrl")

print(plt[["SF contrast Ctrl, NTI-[L,R], Nal-[L,R]"]])

```

## SF AI: Contrasts (reverse)

Contrasts Ctrl, NTI-[L,R], Nal-[L,R] as a table:

```{r sf_contrasts_reverse}

emmc <- contrast(emm, simple = "Op3", method = "trt.vs.ctrl1", reverse=TRUE)
emm_show(emmc)

```

Contrasts Ctrl, NTI-[L,R], Nal-[L,R] as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval).

```{r sf_by_contrasts_reverse, echo=FALSE, fig.width = 8}

plt[["SF contrast Ctrl, NTI-[L,R], Nal-[L,R] reverse"]] <- emmc %>% emm_inorder %>% 
  ggplot(aes(x = interaction(contrast, sep=", ", drop=TRUE), y = .value, fill = contrast)) %>%
  my.stat_eye() +
  geom_hline(yintercept=0, linetype="dashed", color="black") +
  labs(title=myname, x="0-2 sec", y="AI, between groups and ctrl")

print(plt[["SF contrast Ctrl, NTI-[L,R], Nal-[L,R] reverse"]])

```

## SF AI: Contrast of contrasts

Contrast of contrasts Ctrl, NTI-[L,R], Nal-[L,R] as a table:

```{r sf_contrasts_of_contrasts}

emmc_2 <- contrast(emm, simple = "Op3", method = "trt.vs.ctrl")
emmc_2 <- contrast(emmc_2, simple = "contrast", method = "pairwise")

emm_show(emmc_2)


```

Contrast of contrasts Ctrl, NTI-[L,R], Nal-[L,R] as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval).

```{r sf_by_contrast_of_contrasts, echo=FALSE, fig.width = 8}

plt[["SF contrast of contrasts Ctrl, NTI-[L,R], Nal-[L,R]"]] <- emmc %>% emm_inorder %>% 
  ggplot(aes(x = interaction(contrast, sep=", ", drop=TRUE), y = .value, fill = contrast)) %>%
  my.stat_eye() +
  geom_hline(yintercept=0, linetype="dashed", color="black") +
  labs(title=myname, x="0-2 sec", y="AI, Contrast of contrasts")

print(plt[["SF contrast of contrasts Ctrl, NTI-[L,R], Nal-[L,R]"]])

```

Contrast of contrasts NTI, Naloxone, Ctrl 3h as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r  sf_contrasts_of_contrasts_group_vs_ctrl_plot, echo=FALSE, fig.width = 8}

plt[["SF Contrast of contrasts NTI, Naloxone vs Ctrl"]] <- emmc_2 %>% emm_inorder %>% 
  filter(contrast %in% c("(L.NTI - Ctrl) - (R.Nal - Ctrl)", "(R.NTI - Ctrl) - (L.Nal - Ctrl)")) %>%
  ggplot(aes(y = fct_rev(interaction(contrast, sep=", ", drop=TRUE)), x = .value, fill = contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="AI, Contrast of contrasts")

print(plt[["SF Contrast of contrasts NTI, Naloxone vs Ctrl"]])

```


Contrast of contrasts NTI, Naloxone, Ctrl 3h as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r  sf_contrasts_of_contrasts_group_vs_ctrl_plot_second, echo=FALSE, fig.width = 8}

plt[["SF Contrast of contrasts NTI, Naloxone vs Ctrl new"]] <- emmc_2 %>% emm_inorder %>% 
  filter(contrast %in% c("(L.NTI - Ctrl) - (R.NTI - Ctrl)", "(L.Nal - Ctrl) - (R.Nal - Ctrl)")) %>%
  ggplot(aes(y = fct_rev(interaction(contrast, sep=", ", drop=TRUE)), x = .value, fill = contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="AI, Contrast of contrasts")

print(plt[["SF Contrast of contrasts NTI, Naloxone vs Ctrl new"]])

```


Contrast of contrasts NTI, Naloxone, Ctrl 3h as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r sf_contrasts_of_contrasts_group_vs_ctrl_plot_all, echo=FALSE, fig.width = 8}

plt[["SF Contrast of contrasts NTI, Naloxone vs Ctrl all"]] <- emmc_2 %>% emm_inorder %>% 
  ggplot(aes(y = fct_rev(interaction(contrast, sep=", ", drop=TRUE)), x = .value, fill = contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="AI, Contrast of contrasts")

print(plt[["SF Contrast of contrasts NTI, Naloxone vs Ctrl all"]])

```


# Editable PowerPoint plots generated...

```{r pptx, message=TRUE, warning=TRUE, include=FALSE, results='hide'}

myname <- "SF span=0.4 0-2 CI AI Ctrl_NTI_Nal"

doc <- read_pptx()

for(nm in names(plt)) {
  doc <- doc %>%
    add_slide(layout = "Title and Content", master = "Office Theme") %>%
    ph_with(value = rvg::dml(ggobj = plt[[nm]]),
          location = ph_location_type(type = "body"
                                      #, width=S_width, height=S_height
                                      ),
          bg = "transparent" ) %>%
    ph_with(value = nm,
          location = ph_location_type(type = "title") )
}
doc %>% print(target = paste0(myname,".pptx"))

```
