---
title: 'SF: Read and preprocess raw stretch force measurements Ctrl, NTI, Naloxone'
author: "Yaromir Kobikov <kobikov.yaromir@gmail.com>"
date: "Date: `r format(Sys.time(), '%d/%m/%Y')`"
output:
  word_document: default
  html_document:
    toc: true
    toc_float:
      collapsed: false
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}

source("../BayesianPValue.R")

```

The resistance was measured as the amount of mechanical work $W_{contra}$ and $W_{ipsi}$ to stretch the contra- and ipsilesional hindlimbs, where $W(T_{0-2}) = \int_{t=0}^{2} f(t)$ was stretching  force integrated over stretching distance interval from 0 to 10 mm. Asymmetry was assessed as the contra-/ipsilesional asymmetry index $AI_W = log2(W_{contra} / W_{ipsi})$, and as the difference in work performed by the contra- and ipsilesional hindlimb $\Delta W = (W_{contra} - W_{ipsi})$. The control intact rat showed symmetric $W$ pattern; the $W$ for the left and right limbs were calculated instead of $W_{contra}$ and $W_{ipsi}$ for this animal.

## Read stretch force (SF) data 

Read raw sampled forces and match them with rat's descriptions

```{r config_vars, echo=FALSE}

PATH_DIR_ROOT <- "../data"
PATH_FOLDER_FORCE_MEASUREMENT <- "../data/force_measurement/" 
PATH_SF_DATA_CSV <- paste0(PATH_FOLDER_FORCE_MEASUREMENT, "sf_ctrl_nti_nal_data_20230506.csv")

FILE_NAME = '-ForceValues.xlsx'
PATTERN = paste0('*', FILE_NAME)

DESCRIPTION_FILE_NAME <- "SDU-RDPA-Stat_v2.xlsx"
SHEET <- "SDU-RD-Stat-v2" # for description

TEST_NUM_FILES <- 62

```


```{r help_finctions,  echo=FALSE}

correctDate <- Vectorize(function(date, pattern, sep="-") {
  dateSplit <- str_split(date, pattern)[[1]]
  return(paste0(dateSplit[1], sep, dateSplit[2], sep, dateSplit[3]))
})

read.StretchForce <- function(RatFile, show=FALSE) {
  ratName <- sub(FILE_NAME, "", basename(RatFile), fixed = TRUE)
  ratNum <- str_split(ratName, "SDU")[[1]][2]
  ratName <- paste0("SDU", "-", ratNum)
  sheetNames <- RatFile %>% 
    excel_sheets() %>% 
    as_tibble %>% 
    filter(grepl(pattern = "F([0-9]+)", value))
  
  df <- 
    map_df(
      .x = sheetNames$value,
      ~read_excel(path = RatFile, sheet = .x, range = cell_cols("A:C")),
      .id = "replication"
      ) %>% 
    mutate(RatID = ratName) %>% 
    relocate(RatID, .before = replication)
  
  if(show) print(paste0(ratName, " -> ", toString(count(sheetNames)$n), ", ", count(df)$n))
  return(df)
}

my.rwData <- function() {
  
  # if(file.exists(PATH_SF_DATA_CSV)) {
  #   print(paste0("File ", " - ", PATH_SF_DATA_CSV, " - exists"))
  #   return(read_csv(PATH_SF_DATA_CSV, show_col_types = FALSE))
  # }
  print("In process...")
  
  sf <- 
    map_df(
      .x = list.files(path = PATH_FOLDER_FORCE_MEASUREMENT, pattern = PATTERN, full.names = TRUE),
      ~read.StretchForce(.x)
    )
  
  if(length(unique(sf$RatID)) == TEST_NUM_FILES) print(paste0(TEST_NUM_FILES, " - ", "OK"))
  
  # match rat's description with raw force measurements
  rats_description <-
    file.path(PATH_DIR_ROOT, DESCRIPTION_FILE_NAME) %>% 
    read_excel(SHEET, .name_repair = "universal", na = c("", "NA", "NULL")) %>%
    mutate(
      RatID = Rat.ID,
      Dose = factor(Anesthesia.dosage..route, c("40 mg/kg, i.p.", "60 mg/kg, i.p."), c("40", "60")),
      Treatment.4 = ...13,
      WPre = BW.1,
      WPost = BW.2,
      Group3 = ifelse(is.na(Treatment.1), "Ctrl", Treatment.1)
    ) %>% 
     select(
      RatID, Date, Day, Measurement.method, Dose, Treatment.1, Treatment.3, Treatment.4, WPre, WPost, Group3, Operation.side
    ) %>% 
    filter(Measurement.method == "MP") %>%
    mutate(
      Day = replace(Day, which(is.na(Day)), mean(Day, na.rm=TRUE)),
      Date = as.numeric(as.Date(correctDate(Date, "\\."))),
      DateD = Date - min(Date),
      Day = as.numeric(Day),
      DateD = as.numeric(DateD)
    )
  
  sf <-
    merge(sf, rats_description, by=c("RatID"), all.x=TRUE, all.y=TRUE, sort=FALSE) %>%
    drop_na(Treatment.3) %>%
    filter(replication %in% c(7:12, 19:24, 31:36)) %>%  # 3h, 4h, 5h 
    pivot_longer(
      cols = c("Left", "Right"),
      names_to = c("Side"),
      values_to = "SF"
    ) %>%
    mutate(
      SF = SF*(-1),
      Operation.side = recode_factor(Operation.side, Left='L', Right='R'),
      Period = ifelse(replication %in% c(7:12), "3h", 
                      ifelse(replication %in% c(19:24), "4h", "5h")),
      
      
      Trt = ifelse(Period == '3h' & Treatment.3 != 'Saline', 'Ctrl',
                    ifelse(Period == '3h' & Treatment.3 == 'Saline', 'Saline',
                           ifelse(Period == '4h', Treatment.3,
                                  ifelse(Period == '5h' & Treatment.3 == 'Saline', Treatment.4, 'NTI.Nal')))),
      Group3 = ifelse(Trt == "Ctrl" | Period == '4h' & Trt == "Saline", "Ctrl", Trt),
      Group3 = ifelse(Group3 == 'Ctrl', 'Ctrl', paste0(Operation.side, '.', Trt)),
      Group3 = factor(Group3, c("Ctrl", "L.Saline", "R.Saline", "L.NTI", "R.NTI", "L.Nal", "R.Nal", "L.NTI.Nal", "R.NTI.Nal")),
      Trt = paste0(Period, '.', Trt, '.', Operation.side),
      Period = factor(Period, c("3h", "4h", "5h")),
    ) %>% 
    filter(!(Group3 %in% c("L.Saline", "R.Saline", "L.NTI.Nal", "R.NTI.Nal"))) %>% 
    ungroup %>% droplevels(.)
  
  # write_csv(x = sf, PATH_SF_DATA_CSV)
  return(sf)
}

```

```{r}

correctDate <- Vectorize(function(date, pattern, sep="-") {
  dateSplit <- str_split(date, pattern)[[1]]
  return(paste0(dateSplit[1], sep, dateSplit[2], sep, dateSplit[3]))
})

read.StretchForce <- function(RatFile, show=FALSE) {
  ratName <- sub(FILE_NAME, "", basename(RatFile), fixed = TRUE)
  ratNum <- str_split(ratName, "SDU")[[1]][2]
  ratName <- paste0("SDU", "-", ratNum)
  sheetNames <- RatFile %>% 
    excel_sheets() %>% 
    as_tibble %>% 
    filter(grepl(pattern = "F([0-9]+)", value))
  
  df <- 
    map_df(
      .x = sheetNames$value,
      ~read_excel(path = RatFile, sheet = .x, range = cell_cols("A:C")),
      .id = "replication"
      ) %>% 
    mutate(RatID = ratName) %>% 
    relocate(RatID, .before = replication)
  
  if(show) print(paste0(ratName, " -> ", toString(count(sheetNames)$n), ", ", count(df)$n))
  return(df)
}

my.rwData <- function() {
  
  # if(file.exists(PATH_SF_DATA_CSV)) {
  #   print(paste0("File ", " - ", PATH_SF_DATA_CSV, " - exists"))
  #   return(read_csv(PATH_SF_DATA_CSV, show_col_types = FALSE))
  # }
  print("In process...")
  
  sf <- 
    map_df(
      .x = list.files(path = PATH_FOLDER_FORCE_MEASUREMENT, pattern = PATTERN, full.names = TRUE),
      ~read.StretchForce(.x)
    )
  
  if(length(unique(sf$RatID)) == TEST_NUM_FILES) print(paste0(TEST_NUM_FILES, " - ", "OK"))
  
  # match rat's description with raw force measurements
  rats_description <-
    file.path(PATH_DIR_ROOT, DESCRIPTION_FILE_NAME) %>% 
    read_excel(SHEET, .name_repair = "universal", na = c("", "NA", "NULL")) %>%
    mutate(
      RatID = Rat.ID,
      Dose = factor(Anesthesia.dosage..route, c("40 mg/kg, i.p.", "60 mg/kg, i.p."), c("40", "60")),
      Treatment.4 = ...13,
      WPre = BW.1,
      WPost = BW.2,
      Group3 = ifelse(is.na(Treatment.1), "Ctrl", Treatment.1)
    ) %>% 
     select(
      RatID, Date, Day, Measurement.method, Dose, Treatment.1, Treatment.3, Treatment.4, WPre, WPost, Group3, Operation.side
    ) %>% 
    filter(Measurement.method == "MP") %>%
    mutate(
      Day = replace(Day, which(is.na(Day)), mean(Day, na.rm=TRUE)),
      Date = as.numeric(as.Date(correctDate(Date, "\\."))),
      DateD = Date - min(Date),
      Day = as.numeric(Day),
      DateD = as.numeric(DateD)
    )
  
  sf <-
    merge(sf, rats_description, by=c("RatID"), all.x=TRUE, all.y=TRUE, sort=FALSE) %>%
    drop_na(Treatment.3) %>%
    filter(replication %in% c(7:12, 19:24, 31:36)) %>%  # 3h, 4h, 5h 
    pivot_longer(
      cols = c("Left", "Right"),
      names_to = c("Side"),
      values_to = "SF"
    ) %>%
    mutate(
      SF = SF*(-1),
      Operation.side = recode_factor(Operation.side, Left='L', Right='R'),
      Period = ifelse(replication %in% c(7:12), "3h", 
                      ifelse(replication %in% c(19:24), "4h", "5h")),
      
      
      Trt = ifelse(Period == '3h' & Treatment.3 != 'Saline', 'Ctrl',
                    ifelse(Period == '3h' & Treatment.3 == 'Saline', 'Saline',
                           ifelse(Period == '4h', Treatment.3,
                                  ifelse(Period == '5h' & Treatment.3 == 'Saline', Treatment.4, 'NTI.Nal')))),
      Group3 = ifelse(Trt == "Ctrl" | Period == '4h' & Trt == "Saline", "Ctrl", Trt),
      # Group3 = ifelse(Group3 == 'Ctrl', 'Ctrl', paste0(Operation.side, '.', Trt)),
      # Group3 = factor(Group3, c("Ctrl", "L.Saline", "R.Saline", "L.NTI", "R.NTI", "L.Nal", "R.Nal", "L.NTI.Nal", "R.NTI.Nal")),
      Trt = paste0(Period, '.', Trt, '.', Operation.side),
      Period = factor(Period, c("3h", "4h", "5h")),
    ) %>% 
    filter(!(Group3 %in% c("Saline", "NTI.Nal"))) %>% 
    ungroup %>% droplevels(.)  %>% 
    pivot_wider(
      names_from = Side,
      values_from = SF
    )
  
  write_csv(x = sf, PATH_SF_DATA_CSV)
  return(sf)
}
```



```{r input, results='hide'}

myspan <- 0.4
myname0 <- paste0("SF loess(symmetric span=", myspan, ")")

data <- my.rwData()

sf <- 
  data %>%
  rename(MS = Side, repN = replication, OperationSide = Operation.side) %>% 
  select(!Measurement.method) %>% 
  mutate(
    RatID = factor(RatID),
    MS = factor(MS, c("Left", "Right"), c("L", "R")),
    Later = factor(OperationSide == MS, c(FALSE, TRUE), c("Contra", "Ipsi")),
    Trt = factor(Trt),
    repN = factor(as.integer(repN))
  )

# sf[!complete.cases(sf), c("RatID", "Op3", "Trt", "repN", "Later", "SF")] # Any unmatched rats? Any unmeasured forces?
```

The group sizes are (distinct rats only, same rats with different stimulation locations are counted as duplicates)

```{r dataset_n, echo=FALSE}

d.sum <- sf %>% 
  arrange(Group3, Period, OperationSide) %>% 
  group_by(Group3, Period, OperationSide) %>% 
  summarise(rats = length(unique(RatID)), .groups = "drop") %>%
  pivot_wider(names_from=c(Period), values_from = rats)

d.sum %>% 
  flextable %>% 
  fontsize(part = "header", size = 9) %>% 
  autofit

```

## SF, 0-2 sec: Visual inspection of smoothing

<!-- Filter 0-2 sec measurements, taking extra 0.5s for better smoothing. -->

```{r SF_combo_dta}

mydta <- sf %>%
  filter(!is.na(SF)) %>%
  droplevels(.) %>%
  mutate(figName = paste0(RatID, ", ", Trt, ", replicate ", repN)) %>%
  select(figName, Later, Time, SF) %>%
  # filter(figName == "SDU-068, Ctrl, replicate 9") %>%
  group_by(figName)

```

Stretch force figure combining Contra, Ipsi and their difference.

```{r example_12_rep, echo=FALSE, fig.width=12, fig.height=8}

# myspan <- 0.4

name_fig <- "SDU-068, 3h.Ctrl.R, replicate 9"
name_plt <- paste0("raw ", name_fig)

plt[[name_plt]] <- 
  mydta %>%
  filter( figName == name_fig) %>%
  pivot_wider(names_from = Later, values_from = SF) %>%
  mutate( 
    "Contra - Ipsi" = Contra - Ipsi
  ) %>%
  pivot_longer(c("Contra", "Ipsi", "Contra - Ipsi"), names_to = "Limbs", values_to = "SF") %>% 
  ggplot(aes(x = Time, y = SF, group = Limbs, col = Limbs)) + 
  geom_line() + 
  geom_smooth(
    formula = y ~ x, 
    aes(col = paste0("loess ", myspan)), 
    method ="loess", 
    span = myspan, 
    se = FALSE, 
    method.args = list(family="symmetric")
  ) +
  labs(
    title = paste0(myname0, ", ", name_fig), 
    x = "Time (sec)", 
    y = "Stretching force (mg)"
  )

print(plt[[name_plt]])

```

```{r}

# doc <- read_pptx()
# 
# for(nm in names(plt)) {
#   doc <- doc %>%
#     add_slide(
#       layout = "Title and Content",
#       master = "Office Theme"
#     ) %>%
#     ph_with(
#       value = rvg::dml(ggobj = plt[[nm]]),
#       location = ph_location_type(
#         type = "body"
#         #, width=S_width,
#         # height=S_height
#         ),
#       bg = "transparent"
#     ) %>%
#     ph_with(
#       value = nm,
#       location = ph_location_type(type = "title")
#     )
# }
# 
# doc %>% print(target = paste0("SF loess(symmetric span0.4)", ".pptx"))

```

Visually check the smoothing by loess(), varying the "span" to see if alternatives are better than our choice. 

```{r check_loess, include=FALSE}

# myspan.test <- 0.4
# 
# junk <- mydta %>%
#   group_map( ~{
#     theName <- paste(.y)
#     ggplot(data=.x, aes(y = SF, x = Time, group = Later, col = Later)) + 
#       geom_line() + 
#       geom_smooth(formula = y ~ x, aes(col = paste0(myspan.test + 0.1)), method="loess", span = myspan.test + 0.1, se=FALSE, method.args=list(family="symmetric")) +
#       geom_smooth(formula = y ~ x, aes(col = paste0(myspan.test - 0.1)), method="loess", span = myspan.test - 0.1, se=FALSE, method.args=list(family="symmetric")) +
#       geom_smooth(formula = y ~ x, aes(col = paste0(myspan.test)), method="loess", span=myspan.test, se=FALSE, method.args=list(family="symmetric")) +
#       # theme(legend.position = "none") +
#       labs(title=paste(myname0, theName), x="Time (sec)", y="Stretching force (mg)")
#   } ) %>% 
#   setNames(unique(sort(mydta$figName)))
# 
# mydta %>% n_groups()

```

```{r write_pptx_check_loess, echo=FALSE, fig.width=12, fig.height=8}

# for(nm in unique(mydta$figName)) {
#   print(junk[[nm]])
# }
# 
# doc <- read_pptx()
# 
# for(nm in unique(mydta$figName)) {
#   doc <- doc %>%
#     add_slide(
#       layout = "Title and Content",
#       master = "Office Theme"
#     ) %>%
#     ph_with(
#       value = rvg::dml(ggobj = junk[[nm]]),
#       location = ph_location_type(
#         type = "body"
#         #, width=S_width,
#         # height=S_height
#         ),
#       bg = "transparent"
#     ) %>%
#     ph_with(
#       value = nm,
#       location = ph_location_type(type = "title")
#     )
# }
# doc %>% print(target = paste0(myname0, "_0.4_.pptx"))

```

Define smoother for all Time points.

```{r smoother_W_AI}

# 0-1 0.4-1 1-2 0-2 0.4-2

smoother_W <- function(dta, ...) {

  # dtaF <- dta %>% filter(Time < 10.5, !is.na(SF))

  dtaF <- dta %>% filter(!is.na(SF))

  if(nrow(dtaF) < 1 | ncol(dtaF) < 2) {
    print(dta)
    return(data.frame())
  }

  my.sm <- loess(SF~Time, data=dtaF, family="symmetric", span=myspan)

  i_0_1  <- integrate(function(x) predict(my.sm, newdata=x), 0, 1)
  i_0_4_1  <- integrate(function(x) predict(my.sm, newdata=x), 0.4, 1)
  i_1_2 <- integrate(function(x) predict(my.sm, newdata=x), 1, 2)
  i_0_2 <- integrate(function(x) predict(my.sm, newdata=x), 0, 2)
  i_0_4_2 <- integrate(function(x) predict(my.sm, newdata=x), 0.4, 2)

  data.frame(
    dT = c(
      "T_0_1",
      "T_0.4_1",
      "T_1_2",
      "T_0_2",
      "T_0.4_2"
      ),
    W = c(
      i_0_1$value,
      i_0_4_1$value,
      i_1_2$value,
      i_0_2$value,
      i_0_4_2$value
      )
  )
}

```

Remove unneded columns from SF dataset

```{r clean_SF}

sf_ai_dw <-
  sf %>%
  # filter(RatID == "TBI-250", Trt %in% c("UBI.R")) %>%
  select(Trt, OperationSide, Group3, Period, RatID, repN, MS, Later, Day, WPost, DateD, Time, SF) %>%
  ungroup %>%
  arrange(Trt, OperationSide, RatID, repN, Later, Time)

```

Compute work (W) as integrals (0-1 sec, 0.4-1 sec, ... ) of smoothed force measurements. dW = W_Contra - W_Ipsi

```{r compute_W_CI}

sf_CI_dW <- sf_ai_dw %>%
  select( -MS ) %>%
  group_by(Trt, OperationSide, Group3, Period, RatID, repN, Day, WPost, DateD) %>%
  pivot_wider(names_from = Later, values_from = SF) %>%
  mutate( SF = Contra - Ipsi ) %>%
  group_modify(smoother_W) %>%
  ungroup %>%
  droplevels(.)

```

Compute AI = log2(Contra/Ipsi) using integrals (0-1 sec, 0.4-1 sec, ...) of smoothed force measurements.

```{r compute_AI_CI}

sf_CI_AI <- sf_ai_dw %>%
  select( -MS ) %>%
  group_by(Trt, OperationSide, Group3, Period, RatID, repN, Later, Day, WPost, DateD) %>%
  group_modify(smoother_W) %>%
  ungroup %>%
  group_by(RatID, Trt, repN, dT) %>%
  pivot_wider(names_from = Later, values_from = W) %>%
  # spread(Later, W) %>%
  mutate( AI = log2( Contra / Ipsi ) ) %>%
  ungroup %>%
  droplevels(.)

```

Compute work (W) as integrals (0-1 sec, 0.4-1 sec, ...) of smoothed force measurements. dW = W_Left - W_Right

```{r compute_W_LR}

sf_LR_dW <- sf_ai_dw %>%
  select( -Later ) %>%
  group_by(Trt, OperationSide, Group3, Period, RatID, repN, Day, WPost, DateD) %>%
  pivot_wider(names_from = MS, values_from = SF) %>%
  # spread(MS, SF) %>%
  mutate( SF = L - R ) %>%
  group_modify(smoother_W) %>%
  ungroup %>%
  droplevels(.)

```

Compute AI = log2(Left/Right) using integrals (0-1 sec, 0.4-1 sec, ...) of smoothed force measurements.

```{r compute_AI_LR}

sf_LR_AI <- sf_ai_dw %>%
  select( -Later ) %>%
  group_by(Trt, OperationSide, Group3, Period, RatID, repN, MS, Day, WPost, DateD) %>%
  group_modify(smoother_W) %>%
  ungroup %>%
  group_by(RatID, Trt, repN, dT) %>%
  pivot_wider(names_from = MS, values_from = W) %>%
  # spread(MS, W) %>%
  mutate( AI = log2( L / R ) ) %>%
  ungroup %>%
  droplevels(.)

```

Save preprocessed SF

```{r smooth}

myname <- paste0("SF Sp 0-1 0.4-1 1-2 0-2 0.4-2 loess(symmetric span", myspan, ")")

save(sf_CI_dW, sf_CI_AI, sf_LR_dW, sf_LR_AI, sf, file=paste0(myname, "_Ctrl_NTI_Nal_v3.RData"))

```
