---
title: "Vertical Analysis PAS: Ctrl, BNI, FNA (hand, machine)"
author: "Yaromir Kobikov <kobikov.yaromir@gmail.com>"
date: "Date: `r format(Sys.time(), '%d/%m/%Y')`"
output:
  word_document: default
  html_document:
    toc: true
    toc_float:
      collapsed: false
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
source("../BayesianPValue.R")
```

# PAS (Magnitude of Postural asymmetry)

Values in “+”.

# Read Data

Read from Excel file.

```{r input}

file_name <- "data/SDU-RDPA-Stat_v2.xlsx"
sheet <- "SDU-RD-Stat-v2"

my.seed <- 20231201 # reproducible Bayesian fit

myname0 <- "PAS"

main_dir <- "../" # path to the base folder, containing data and results
path_rds <- "rds/vertical_analysis/pas_bni_fna_ctrl/" # folder to store the results 
DESIGN <- "RD" # only reverse design data will be used
full_rds_path = paste0(main_dir, path_rds)

dir.create(file.path(main_dir, path_rds), showWarnings = FALSE)

data <-
  file.path(main_dir, file_name) %>% 
  read_excel(sheet, .name_repair = "universal", na = c("", "NA", "NULL")) %>%
  mutate(
    RatID = Rat.ID,
    Side = recode_factor(Operation.side, Left='L', Right='R'),
    Dose = factor(Anesthesia.dosage..route, c("40 mg/kg, i.p.", "60 mg/kg, i.p."), c("40", "60")),
    Treatment.4 = factor(...13),
    WPre = BW.1,
    WPost = BW.2,
    Group3 = ifelse(is.na(Treatment.1), "Ctrl", Treatment.1)
    # Trt4 = ifelse(is.na(Treatment.1) & (!is.na(Treatment.3) & (Treatment.3 != 'Saline')), "Ctrl", Treatment.3)
  ) %>% 
  select(
    RatID, Date, Side, Measurement.method, Dose, Treatment.1, Treatment.3, Treatment.4, WPre, WPost, Group3,
    starts_with(c("PA1.", "PA2.", "PA3.", "PA4.", "PA5.", "PA6."))
  ) %>% 
  pivot_longer(
    cols = PA1.1:PA6.6,
    names_to = c("Time"),
    names_pattern = "PA(.)",
    values_to = "PA"
  ) %>% 
  mutate(
    RatID = factor(RatID),
    Time = factor(Time, c("1", "2", "3", "4", "5", "6"), c("0h", "3h", "3h20m", "4h", "4h20m", "5h")),
    Group4 = ifelse(Group3 == 'Ctrl' & Time == '3h' & (!is.na(Treatment.3) & (Treatment.3 != 'Saline')), 'Ctrl', Treatment.3),
    Group4.Side = ifelse(Group4 != 'Ctrl', paste0(Side, '.', Group4), Group4),
    Group4 = factor(Group4, c("Ctrl", "Saline", "NTI", "Nal")),
    Group4.Side = factor(Group4.Side, c("Ctrl", "L.Saline", "R.Saline", "L.NTI", "R.NTI", "L.Nal", "R.Nal")),
    Group3 = ifelse(Group3 == 'Ctrl', 'Ctrl', paste0(Side, '.', Group3)),
    Group3 = factor(Group3, c("Ctrl", "L.BNI", "R.BNI", "L.FNA", "R.FNA")),
    MPA = abs(PA)
  ) %>%
  drop_na("PA") %>%
  ungroup %>% droplevels(.)

data_hand <-
  data %>%
  filter(Measurement.method == "Hand") %>% 
  droplevels(.)

data_machine <-
  data %>%
  filter(Measurement.method == "MP") %>% 
  droplevels(.)

```
```{r splt_data, echo=FALSE}

data_hand <- data_hand %>% 
  filter(Time == '0h' | Time == '3h') %>% 
  droplevels(.)
data_machine <- data_machine %>%
  filter(Time == '0h' | Time == '3h') %>%
  droplevels(.)

```

# (Hand) Ctrl, BNI, FNA

```{r input2, echo=FALSE}

data_hand %>% 
  arrange(Group3, Time) %>% 
  group_by(Group3, Time) %>% 
  summarise(rats = length(unique(RatID)), .groups = "drop") %>%
  # select(!Time) %>%
  pivot_wider(names_from=c(Time), values_from=rats) %>%
  # replace_na(list("3h"=0, "4h"=0)) %>%
  flextable %>% autofit

d1 <- data_hand

```

# (Hand) Analyse Ctrl, BNI, FNA.

## PAS: Student Model

Prior predictive check

```{r hand_pas_check_prior}

myname <- paste0(myname0, "_Ctrl_BNI_FNA_Hand")

std.prior <- brm(
  data = d1,
  family = gaussian,
   bf(
     PA ~ 0 + Group3:Time + (1|RatID),
     sigma ~ 0 + Group3:Time
   ),
  prior = c(prior(normal(0, 3), class = "b"),
            prior(normal(0, 3), class = "b", dpar="sigma")),
  seed = my.seed, 
  chains = my.cores, 
  cores = my.cores, 
  iter = 4e4,
  sample_prior = "only",
  file = paste0(full_rds_path, "ctrl_bni_fna_check_prior.rds"),
  file_refit = "on_change"
)

cond_eff <- conditional_effects(std.prior, 
                                "Group3", 
                                method="fitted",
                                conditions=make_conditions(d1, vars = c("Time")))

plt[["Ctrl,BNI,FNA PAS prior vs data (hand)"]] <- plot(cond_eff, 
                                       points = TRUE, 
                                       point_args = list(width = 0.1, shape="o", col="red"),
                                       plot=FALSE)[[1]] + 
                                  geom_hline(yintercept=0, linetype="dashed", color="black")

set.seed(2)
plt[["Ctrl,BNI,FNA PAS prior pp_check (hand)"]] <- pp_check(std.prior, ndraws = 11)

print(cond_eff[[1]])
print(plt[["Ctrl,BNI,FNA PAS prior vs data (hand)"]])
print(plt[["Ctrl,BNI,FNA PAS prior pp_check (hand)"]])

```

Model fit and QC:

```{r hand_pas_model_summary, echo=FALSE, fig.width = 10}

std.fit <-  update(std.prior, 
                   sample_prior = "yes",
                   # control = list(adapt_delta = 0.99),
                   seed = my.seed, 
                   cores = my.cores,
                   file = paste0(full_rds_path, "ctrl_bni_fna_model_summary.rds"),
                   file_refit = "on_change")
summary(std.fit)

```

## PAS: MCMC conversion diagnostics

Posterior predictive check

```{r hand_pas_MCMC_ppcheck}

set.seed(2) # reproducible pp_check

plt[["Ctrl,BNI,FNA PAS pp_check (hand)"]] <- pp_check(std.fit, ndraws = 21)

print(plt[["Ctrl,BNI,FNA PAS pp_check (hand)"]])

```

Autocorrelations

```{r hand_pas_MCMC_ac}

plt[["Ctrl,BNI,FNA PAS ac (hand)"]] <- stan_ac(std.fit$fit)

print(plt[["Ctrl,BNI,FNA PAS ac (hand)"]])

```

## PAS: Estimated model marginals

Estimated model medians +- 95% HPDCI (HPDCI = highest posterior density continuous interval) as a table:

```{r hand_pas_emm}

emm <- emmeans(std.fit, ~ Group3:Time, regrid = "response", nesting = NULL)
emm_show(emm)

```

Estimated model means as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_pas_emm_plot, echo=FALSE, fig.width = 8}

plt[["Ctrl,BNI,FNA PAS emm (hand)"]] <- emm %>% emm_inorder %>%
  ggplot(aes(y = fct_rev(interaction(Group3, Time, sep=", ", drop=TRUE)), x = .value, fill = Group3)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  # geom_vline(xintercept=threshold, linetype="dashed", color="black") +
  # geom_vline(xintercept=-threshold, linetype="dashed", color="black") +
  labs(title=myname, y="", x="PAS (mm) Ctrl,BNI,FNA")

print(plt[["Ctrl,BNI,FNA PAS emm (hand)"]])

```

Estimated model means as a median +- 95% HPDCI ("x" - mean values of measurements for each rat)

```{r points_pas_emm_plot, echo=FALSE, fig.width=8}

plt[["Ctrl,BNI,FNA PAS emm (hand) with Data Points"]] <- 
  plt[["Ctrl,BNI,FNA PAS emm (hand)"]] +
    geom_point(
      pch = 4,
      position = position_nudge(y=0.15),
      data = {
        d1 %>%
          group_by(RatID, Group3, Time) %>%
          summarise(.value = mean(PA), .groups = "drop")
      },
      aes(x=.value))

print(plt[["Ctrl,BNI,FNA PAS emm (hand) with Data Points"]])

```

## PAS: Contrasts

Contrasts BI vs SS as a table:

```{r hand_pas_contrasts}

emmc <- rbind(contrast(emm, simple = "Group3", method = "trt.vs.ctrl1"),
              contrast(emm, simple = "Time", method = "consec"))
emm_show(emmc)

```

Contrasts BI vs SS as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_pas_plot, echo=FALSE, fig.width = 8}

plt[["Ctrl,BNI,FNA PAS by Side (hand)"]] <- emmc %>% emm_inorder %>% filter(Group3 == ".") %>% 
  ggplot(aes( y = fct_rev(interaction(Time, contrast, sep=", ", drop=TRUE)), x=.value, fill=contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="PAS in mm, contrast: Ctrl vs BNI, FNA")

print(plt[["Ctrl,BNI,FNA PAS by Side (hand)"]])

```

Contrasts "between time" as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_ctrl_bni_fna_pas_by_time, echo=FALSE, fig.width = 8}

plt[["Ctrl, BNI, FNA PAS by Time (hand)"]] <- emmc %>% emm_inorder %>% filter(Time == ".") %>% 
  ggplot(aes(y = fct_rev(interaction(Group3, contrast, sep=", ", drop=TRUE)), x = .value, fill = Group3)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="PAS in mm, contrast by time")

print(plt[["Ctrl, BNI, FNA PAS by Time (hand)"]])

```

# (Machine) Ctrl, BNI, FNA

```{r input2_machine, echo=FALSE}

data_machine %>% 
  arrange(Group3, Time) %>% 
  group_by(Group3, Time) %>% 
  summarise(rats = length(unique(RatID)), .groups = "drop") %>%
  # select(!Time) %>%
  pivot_wider(names_from=c(Time), values_from=rats) %>%
  # replace_na(list("3h"=0, "4h"=0)) %>%
  flextable %>% autofit

d1 <- data_machine

```

# (Machine) Analyse Ctrl, BNI, FNA.

## PAS: Student Model

Prior predictive check

```{r machine_pas_check_prior}

myname <- paste0(myname0, "_Ctrl_BNI_FNA_machine")

std.prior <- brm(
  data = d1,
  family = gaussian,
   bf(
     PA ~ 0 + Group3:Time + (1|RatID),
     sigma ~ 0 + Group3:Time
   ),
  prior = c(prior(normal(0, 3), class = "b"),
            prior(normal(0, 3), class = "b", dpar="sigma")),
  seed = my.seed, 
  chains = my.cores, 
  cores = my.cores, 
  iter = 4e4,
  sample_prior = "only",
  file = paste0(full_rds_path, "machine_ctrl_bni_fna_check_prior.rds"),
  file_refit = "on_change"
)

cond_eff <- conditional_effects(std.prior, 
                                "Group3", 
                                method="fitted",
                                conditions=make_conditions(d1, vars = c("Time")))

plt[["Ctrl,BNI,FNA PAS prior vs data (machine)"]] <- plot(cond_eff, 
                                       points = TRUE, 
                                       point_args = list(width = 0.1, shape="o", col="red"),
                                       plot=FALSE)[[1]] + 
                                  geom_hline(yintercept=0, linetype="dashed", color="black")

set.seed(2)
plt[["Ctrl,BNI,FNA PAS prior pp_check (machine)"]] <- pp_check(std.prior, ndraws = 11)

print(cond_eff[[1]])
print(plt[["Ctrl,BNI,FNA PAS prior vs data (machine)"]])
print(plt[["Ctrl,BNI,FNA PAS prior pp_check (machine)"]])

```

Model fit and QC:

```{r machine_pas_model_summary, echo=FALSE, fig.width = 10}

std.fit <-  update(std.prior, 
                   sample_prior = "yes",
                   # control = list(adapt_delta = 0.99),
                   seed = my.seed, 
                   cores = my.cores,
                   file = paste0(full_rds_path, "machine_ctrl_bni_fna_model_summary.rds"),
                   file_refit = "on_change")
summary(std.fit)

```

## PAS: MCMC conversion diagnostics

Posterior predictive check

```{r machine_pas_MCMC_ppcheck}

set.seed(2) # reproducible pp_check

plt[["Ctrl,BNI,FNA PAS pp_check (machine)"]] <- pp_check(std.fit, ndraws = 21)

print(plt[["Ctrl,BNI,FNA PAS pp_check (machine)"]])

```

Autocorrelations

```{r machine_pas_MCMC_ac}

plt[["Ctrl,BNI,FNA PAS ac (machine)"]] <- stan_ac(std.fit$fit)

print(plt[["Ctrl,BNI,FNA PAS ac (machine)"]])

```

## PAS: Estimated model marginals

Estimated model medians +- 95% HPDCI (HPDCI = highest posterior density continuous interval) as a table:

```{r machine_pas_emm}

emm <- emmeans(std.fit, ~ Group3:Time, regrid = "response", nesting = NULL)
emm_show(emm)

```

Estimated model means as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r machine_pas_emm_plot, echo=FALSE, fig.width = 8}

plt[["Ctrl,BNI,FNA PAS emm (machine)"]] <- emm %>% emm_inorder %>%
  ggplot(aes(y = fct_rev(interaction(Group3, Time, sep=", ", drop=TRUE)), x = .value, fill = Group3)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  # geom_vline(xintercept=threshold, linetype="dashed", color="black") +
  # geom_vline(xintercept=-threshold, linetype="dashed", color="black") +
  labs(title=myname, y="", x="PAS (mm) Ctrl,BNI,FNA")

print(plt[["Ctrl,BNI,FNA PAS emm (machine)"]])

```

Estimated model means as a median +- 95% HPDCI ("x" - mean values of measurements for each rat)

```{r machine_points_pas_emm_plot, echo=FALSE, fig.width=8}

plt[["Ctrl,BNI,FNA PAS emm (machine) with Data Points"]] <- 
  plt[["Ctrl,BNI,FNA PAS emm (machine)"]] +
    geom_point(
      pch = 4,
      position = position_nudge(y=0.15),
      data = {
        d1 %>%
          group_by(RatID, Group3, Time) %>%
          summarise(.value = mean(PA), .groups = "drop")
      },
      aes(x=.value))

print(plt[["Ctrl,BNI,FNA PAS emm (machine) with Data Points"]])

```

## PAS: Contrasts

Contrasts BI vs SS as a table:

```{r machine_pas_contrasts}

emmc <- rbind(contrast(emm, simple = "Group3", method = "trt.vs.ctrl1"),
              contrast(emm, simple = "Time", method = "consec"))
emm_show(emmc)

```

Contrasts BI vs SS as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r machine_pas_plot, echo=FALSE, fig.width = 8}

plt[["Ctrl,BNI,FNA PAS by Side (machine)"]] <- emmc %>% emm_inorder %>% filter(Group3 == ".") %>% 
  ggplot(aes( y = fct_rev(interaction(Time, contrast, sep=", ", drop=TRUE)), x=.value, fill=contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="PAS in mm, contrast: Ctrl vs BNI, FNA")

print(plt[["Ctrl,BNI,FNA PAS by Side (machine)"]])

```

Contrasts "between time" as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r machine_ctrl_bni_fna_pas_by_time, echo=FALSE, fig.width = 8}

plt[["Ctrl, BNI, FNA PAS by Time (machine)"]] <- emmc %>% emm_inorder %>% filter(Time == ".") %>% 
  ggplot(aes(y = fct_rev(interaction(Group3, contrast, sep=", ", drop=TRUE)), x = .value, fill = Group3)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="PAS in mm, contrast by time")

print(plt[["Ctrl, BNI, FNA PAS by Time (machine)"]])

```


# Editable PowerPoint plots generated...

```{r pptx, message=TRUE, warning=TRUE, include=FALSE, results='hide'}

myname <- paste0(myname0, "_Ctrl_BNI_FNA")

doc <- read_pptx()

for(nm in names(plt)) {
  doc <- doc %>%
    add_slide(layout = "Title and Content", master = "Office Theme") %>%
    ph_with(value = rvg::dml(ggobj = plt[[nm]]),
          location = ph_location_type(type = "body"
                                      #, width=S_width, height=S_height
                                      ),
          bg = "transparent" ) %>%
    ph_with(value = nm,
          location = ph_location_type(type = "title") )
}
doc %>% print(target = paste0(myname,".pptx"))

```
