---
title: "Bilateral rhizotomy. Analyse MPA UBI vs SO (L, R; hand, machine)"
author: "Yaromir Kobikov <kobikov.yaromir@gmail.com>"
date: "11/2/2021"
output:
 word_document: default
 html_document:
  toc: true
  toc_float:
   collapsed: false
editor_options:
 chunk_output_type: inline
---

```{r setup, include=FALSE}
source("../../BayesianPValue.R")
```

# MPA (Magnitude of Postural asymmetry)

Values in “+”.

# Read Data

Read from Excel file.

```{r input}

rds_folder_name <- "../../rds/bilateral_rhizotomy/3_groups/mpa/"

file_name <- "../../data/SemiAutoADX-masterfile-210807.xlsx"
sheet <- "MasterFile"

my.seed <- 103592321 # reproducible Bayessian fit

myname0 <- "MPA"

data <- 
  read_excel(file_name, sheet) %>%
  filter(`Treatment 1` == "Spinalization") %>% 
  select(RatID, Operation, `Operation side`, `Measuerment method`, starts_with(c("PA3.", "PA4."))) %>% 
  mutate(PA3.6 = as.numeric(PA3.6)) %>% 
  filter(rowSums(is.na(.)) < 6) %>% 
  pivot_longer(
    cols = PA3.1:PA4.6,
    names_to = c("Time"),
    names_pattern = "PA(.)",
    values_to = "PA"
  ) %>%
  mutate(RatID = factor(RatID),
         Side = factor(`Operation side`, c("Left", "Right"), c("L", "R")),
         Time = factor(Time, c("3", "4"), c("3h0m", "3h15m")),
         Trt3 = paste0(Side, Operation),
         Trt3 = replace(Trt3, Operation == "SO", "SO"),
         Trt3 = factor(Trt3, c("SO", "LUBI", "RUBI")),
         MPA = abs(PA)) %>%
  ungroup %>% droplevels(.)

data_hand <-
  data %>%
  filter(`Measuerment method` == "Hand") %>% 
  droplevels(.)

data_machine <-
  data %>%
  filter(`Measuerment method` == "MP") %>% 
  droplevels(.)

```

The group sizes are (distinct rats only, same rats with different stimulation locations are counted as duplicates)

```{r input2, echo=FALSE}

data %>% 
  arrange(Trt3, Time) %>% 
  group_by(Trt3, Time, `Measuerment method`) %>% 
  summarise(rats = length(unique(RatID)), .groups = "drop") %>%
  pivot_wider(names_from=c(Time), values_from=rats) %>% 
  flextable %>% autofit

```

# (Hand) Analyse Sham: L-SO vs R-SO surgery

If "Left SO" is not significantly different from "Right SO" group we can merge them into single "SO" group to test against "UBI".

## MPA: Student Model

Prior predictive check

```{r hand_so_mpa_check_prior}

data_hand_SO <- 
  data_hand %>%
  filter(Operation == 'SO') %>% 
  droplevels(.)

myname <- paste0(myname0, "_SO_Hand")

std.prior <- brm(
  data = data_hand_SO,
  family = student,
  MPA ~ 0 + Time:Side + (1|RatID),
  prior = c(prior(student_t(3, 0, 10), class = "sigma"),
            prior(normal(0, 3), class = "b")),
  seed = my.seed, 
  chains = my.cores, 
  cores = my.cores, 
  iter = 4e4,
  sample_prior = "only",
  file = paste0(rds_folder_name, "so_check_prior.rds"),
  file_refit = "on_change"
)

cond_eff <- conditional_effects(std.prior, 
                                "Side", 
                                method="fitted", 
                                conditions=make_conditions(data_hand_SO, vars = c("Time")))

plt[["SO MPA prior vs data (hand)"]] <- plot(cond_eff, 
                                       points = TRUE, 
                                       point_args = list(width = 0.1, shape="o", col="red"),
                                       plot=FALSE)[[1]] + 
                                  geom_hline(yintercept=0, linetype="dashed", color="black")

set.seed(2)
plt[["SO MPA prior pp_check (hand)"]] <- pp_check(std.prior, ndraws = 11)

print(cond_eff[[1]])
print(plt[["SO MPA prior vs data (hand)"]])
print(plt[["SO MPA prior pp_check (hand)"]])

```

Model fit and QC:

```{r hand_so_mpa_model_summary, echo=FALSE, fig.width = 10}

std.fit <-  update(std.prior, 
                   sample_prior = "yes",
                   control = list(adapt_delta = 0.999),
                   seed = my.seed, 
                   cores = my.cores,
                   file = paste0(rds_folder_name, "so_model_summary.rds"),
                   file_refit = "on_change")
summary(std.fit)

```

## MPA: MCMC conversion diagnostics

Posterior predictive check

```{r hand_so_mpa_MCMC_ppcheck}

set.seed(2) # reproducible pp_check

plt[["SO MPA pp_check (hand)"]] <- pp_check(std.fit, ndraws = 21)

print(plt[["SO MPA pp_check (hand)"]])

```

Autocorrelations

```{r hand_so_mpa_MCMC_ac}

plt[["SO MPA ac (hand)"]] <- stan_ac(std.fit$fit)

print(plt[["SO MPA ac (hand)"]])

```

## MPA: Estimated model marginals

Estimated model medians +- 95% HPDCI (HPDCI = highest posterior density continuous interval) as a table:

```{r hand_so_mpa_emm}

emm <- emmeans(std.fit, ~ Side*Time, transform = "response", nesting = NULL)
emm_show(emm)

```

Estimated model means as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_so_mpa_emm_plot, echo=FALSE, fig.width = 8}

plt[["SO MPA emm (hand)"]] <- emm %>% emm_inorder %>%
  ggplot(aes(y = fct_rev(interaction(Side, Time, sep=", ", drop=TRUE)), x = .value, fill = Side)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  # geom_vline(xintercept=threshold, linetype="dashed", color="black") +
  # geom_vline(xintercept=-threshold, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA (mm) SO")

print(plt[["SO MPA emm (hand)"]])

```

Estimated model means as a median +- 95% HPDCI ("x" - mean values of measurements for each rat)

```{r points_hand_so_mpa_emm_plot, echo=FALSE, fig.width=8}

plt[["SO MPA emm (hand) with Data Points"]] <- 
  plt[["SO MPA emm (hand)"]] +
    geom_point(
      pch = 4,
      position = position_jitterdodge(dodge.width = 0.6, jitter.width = 0.6, seed = 2),
      data = {
        data_hand_SO %>%
          group_by(RatID, Time, Side) %>%
          summarise(.value = mean(MPA), .groups = "drop")
      },
      aes(x=.value, y = as.numeric(fct_rev(interaction(Side, Time, sep=", ", drop=TRUE)))+0.2))

print(plt[["SO MPA emm (hand) with Data Points"]])

```

## MPA: Contrasts

Contrasts BI vs SS as a table:

```{r hand_so_mpa_contrasts}

emmc <- rbind(contrast(emm, simple = "Side", method = "revpairwise"),
              contrast(emm, simple = "Time", method = "consec"))

emm_show(emmc)

```

Contrasts BI vs SS as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_so_mpa_plot, echo=FALSE, fig.width = 8}

plt[["SO MPA by Side (hand)"]] <- emmc %>% emm_inorder %>% filter(Side == ".") %>%
  ggplot(aes( y = fct_rev(interaction(Time, contrast, sep=", ", drop=TRUE)), x=.value, fill=contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA in mm, contrast: L-SO vs R-SO")

print(plt[["SO MPA by Side (hand)"]])

```

Contrasts "between time" as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_so_mpa_by_time, echo=FALSE, fig.width = 8}

plt[["SO MPA by Time (hand)"]] <- emmc %>% emm_inorder %>% filter(Time == ".") %>% 
  ggplot(aes(y = fct_rev(interaction(Side, contrast, sep=", ", drop=TRUE)), x = .value, fill = contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA in mm, contrast: Time")

print(plt[["SO MPA by Time (hand)"]])

```

Contrasts BI vs SS as a table:

```{r hand_so_mpa_contrasts_3_15}

emmc <- rbind(contrast(emm, simple = "Side", method = "revpairwise"),
              contrast(emm, simple = "Time", method = "consec", reverse = TRUE))

emm_show(emmc)

```

Contrasts "between time" as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_so_mpa_by_time_3_15, echo=FALSE, fig.width = 8}

plt[["SO MPA by Time 3h0m - 3h15m (hand)"]] <- emmc %>% emm_inorder %>% filter(Time == ".") %>% 
  ggplot(aes(y = fct_rev(interaction(Side, contrast, sep=", ", drop=TRUE)), x = .value, fill = contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA in mm, contrast: Time")

print(plt[["SO MPA by Time 3h0m - 3h15m (hand)"]])

```

Since "Left SO" is not significantly different from "Right SO" we can merge all sham rats into single "SO" group to test against "Left UBI" and "Right UBI".

# (Hand) Analyse L-UBI vs R-UBI vs SO(L+R)

## MPA: Student Model

Prior predictive check

```{r hand_ubi_mpa_check_prior}

myname <- paste0(myname0, "_UBI_SO_Hand")

std.prior <- brm(
  data = data_hand,
  family = student,
  MPA ~ 0 + Time:Trt3 + (1|RatID),
  prior = c(prior(student_t(3, 0, 10), class = "sigma"),
            prior(normal(0, 3), class = "b")),
  # control = list(adapt_delta=0.9),
  seed = my.seed, 
  chains = my.cores, 
  cores = my.cores, 
  iter = 4e4,
  sample_prior = "only",
  file = paste0(rds_folder_name, "ubi_check_prior.rds"),
  file_refit = "on_change"
)

cond_eff <- conditional_effects(std.prior, 
                                "Trt3", 
                                method="fitted", 
                                conditions=make_conditions(data_hand, vars = c("Time")))

plt[["UBI MPA prior vs data (hand)"]] <- plot(cond_eff, 
                                       points = TRUE, 
                                       point_args = list(width = 0.1, shape="o", col="red"),
                                       plot=FALSE)[[1]] + 
                                  geom_hline(yintercept=0, linetype="dashed", color="black")

set.seed(2)
plt[["UBI MPA prior pp_check (hand)"]] <- pp_check(std.prior, ndraws = 11)

print(cond_eff[[1]])
print(plt[["UBI MPA prior vs data (hand)"]])
print(plt[["UBI MPA prior pp_check (hand)"]])

```

Model fit and QC:

```{r hand_ubi_mpa_model_summary, echo=FALSE, fig.width = 10}

std.fit <-  update(std.prior, 
                   sample_prior = "yes",
                   # control = list(adapt_delta=0.95),
                   seed = my.seed, 
                   cores = my.cores,
                   file = paste0(rds_folder_name, "ubi_model_summary.rds"),
                   file_refit = "on_change")
summary(std.fit)

```

## MPA: MCMC conversion diagnostics

Posterior predictive check

```{r hand_ubi_mpa_MCMC_ppcheck}

set.seed(2) # reproducible pp_check

plt[["UBI MPA pp_check (hand)"]] <- pp_check(std.fit, ndraws = 21)

print(plt[["UBI MPA pp_check (hand)"]])

```

Autocorrelations

```{r hand_ubi_mpa_MCMC_ac}

plt[["UBI MPA ac (hand)"]] <- stan_ac(std.fit$fit)

print(plt[["UBI MPA ac (hand)"]])

```

## MPA: Estimated model marginals

Estimated model medians +- 95% HPDCI (HPDCI = highest posterior density continuous interval) as a table:

```{r hand_ubi_mpa_emm}

emm <- emmeans(std.fit, ~ Trt3*Time, transform = "response", nesting = NULL)
emm_show(emm)

```

Estimated model means as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_ubi_mpa_emm_plot, echo=FALSE, fig.width = 8}

plt[["UBI MPA emm (hand)"]] <- emm %>% emm_inorder %>%
  ggplot(aes(y = fct_rev(interaction(Trt3, Time, sep=", ", drop=TRUE)), x = .value, fill = Trt3)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept = 0, linetype="dashed", color="black") +
  # geom_vline(xintercept = threshold, linetype="dashed", color="black") +
  # geom_vline(xintercept = -threshold, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA (mm), UBI")

print(plt[["UBI MPA emm (hand)"]])

```

Estimated model means as a median +- 95% HPDCI ("x" - mean values of measurements for each rat)

```{r points_hand_ubi_mpa_emm_plot, echo=FALSE, fig.width=8}

plt[["UBI MPA emm (hand) with Data Points"]] <- 
  plt[["UBI MPA emm (hand)"]] +
    geom_point(
      pch = 4,
      position = position_jitterdodge(dodge.width = 0.6, jitter.width = 0.6, seed = 2),
      data = {
        data_hand %>%
          group_by(RatID, Time, Trt3) %>%
          summarise(.value = mean(MPA), .groups = "drop")
      },
      aes(x=.value, y = as.numeric(fct_rev(interaction(Trt3, Time, sep=", ", drop=TRUE)))+0.2))

print(plt[["UBI MPA emm (hand) with Data Points"]])

```

## MPA: Contrasts

Contrasts BI vs SS as a table:

```{r hand_ubi_mpa_contrasts}

emmc <- rbind(contrast(emm, simple = "Trt3", method = "revpairwise"),
              contrast(emm, simple = "Time", method = "consec"))

emm_show(emmc)

```

Contrasts BI vs SS as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_ubi_mpa_plot, echo=FALSE, fig.width = 8}

plt[["UBI MPA by Trt3 (hand)"]] <- emmc %>% emm_inorder %>% filter(Trt3 == ".") %>%
  ggplot(aes( y = fct_rev(interaction(Time, contrast, sep=", ", drop=TRUE)), x=.value, fill=contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA in mm, contrast: SO vs RUBI VS LUBI")

print(plt[["UBI MPA by Trt3 (hand)"]])

```

Contrasts "between time" as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_ubi_mpa_by_time, echo=FALSE, fig.width = 8}

plt[["UBI MPA by Time (hand)"]] <- emmc %>% emm_inorder %>% filter(Time == ".") %>% 
  ggplot(aes(y = fct_rev(interaction(Trt3, contrast, sep=", ", drop=TRUE)), x = .value, fill = Trt3)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA in mm, contrast: Time")

print(plt[["UBI MPA by Time (hand)"]])

```

Contrasts BI vs SS as a table:

```{r hand_ubi_mpa_contrasts_3_15}

emmc <- rbind(contrast(emm, simple = "Trt3", method = "revpairwise"),
              contrast(emm, simple = "Time", method = "consec", reverse = TRUE))

emm_show(emmc)

```

Contrasts "between time" as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_ubi_mpa_by_time_3_15, echo=FALSE, fig.width = 8}

plt[["UBI MPA by Time 3h0m - 3h15m (hand)"]] <- emmc %>% emm_inorder %>% filter(Time == ".") %>% 
  ggplot(aes(y = fct_rev(interaction(Trt3, contrast, sep=", ", drop=TRUE)), x = .value, fill = Trt3)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA in mm, contrast: Time")

print(plt[["UBI MPA by Time 3h0m - 3h15m (hand)"]])

```

Contrast of contrasts:

```{r hand_ubi_mpa_contrasts_of_contrasts}
emmc_2 <- contrast(emm, simple = "Trt3", method = "pairwise")
emmc_2 <- contrast(emmc_2, simple = "Time", method = "pairwise")
emm_show(emmc_2)

```

Contrast of contrasts as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_ubi_mpa_by_time_of_contrasts, echo=FALSE, fig.width = 8}

plt[["UBI MPA 3h (LUBI–RUBI) vs 3h15m (LUBI–RUBI) (hand)"]] <- emmc_2 %>% emm_inorder %>% 
  ggplot(aes(y = fct_rev(interaction(contrast1, contrast, sep=", ", drop=TRUE)), x = .value, fill = contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA in mm, Contrast of contrasts")

print(plt[["UBI MPA 3h (LUBI–RUBI) vs 3h15m (LUBI–RUBI) (hand)"]])

```

Contrast of contrasts reverse:

```{r hand_ubi_mpa_contrasts_of_contrasts_reverse}
emmc_2 <- contrast(emm, simple = "Trt3", method = "revpairwise")
emmc_2 <- contrast(emmc_2, simple = "Time", method = "pairwise")
emm_show(emmc_2)

```

Contrast of contrasts reverse as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_ubi_mpa_by_time_of_contrasts_reverse, echo=FALSE, fig.width = 8}

plt[["UBI MPA 3h (LUBI–RUBI) vs 3h15m (LUBI–RUBI) (hand) reverse"]] <- emmc_2 %>% emm_inorder %>% 
  ggplot(aes(y = fct_rev(interaction(contrast1, contrast, sep=", ", drop=TRUE)), x = .value, fill = contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA in mm, Contrast of contrasts")

print(plt[["UBI MPA 3h (LUBI–RUBI) vs 3h15m (LUBI–RUBI) (hand) reverse"]])

```

# (Machine) Analyse Sham: L-SO vs R-SO surgery

If "Left SO" is not significantly different from "Right SO" group we can merge them into single "SO" group to test against "UBI".

## MPA: Student Model

Prior predictive check

```{r machine_so_mpa_check_prior}

data_machine_SO <- 
  data_machine %>%
  filter(Operation == 'SO') %>% 
  droplevels(.)

myname <- paste0(myname0, "_SO_MP")

std.prior <- brm(
  data = data_machine_SO,
  family = student,
  MPA ~ 0 + Time:Side + (1|RatID),
  prior = c(prior(student_t(3, 0, 10), class = "sigma"),
            prior(normal(0, 3), class = "b")),
  seed = my.seed, 
  chains = my.cores, 
  cores = my.cores, 
  iter = 4e4,
  sample_prior = "only",
  file = paste0(rds_folder_name, "so_check_prior_machine.rds"),
  file_refit = "on_change"
)

cond_eff <- conditional_effects(std.prior, 
                                "Side", 
                                method="fitted", 
                                conditions=make_conditions(data_machine_SO, vars = c("Time")))

plt[["SO MPA prior vs data (Machine)"]] <- plot(cond_eff, 
                                       points = TRUE, 
                                       point_args = list(width = 0.1, shape="o", col="red"),
                                       plot=FALSE)[[1]] + 
                                  geom_hline(yintercept=0, linetype="dashed", color="black")

set.seed(2)
plt[["SO MPA prior pp_check (Machine)"]] <- pp_check(std.prior, ndraws = 11)

print(cond_eff[[1]])
print(plt[["SO MPA prior vs data (Machine)"]])
print(plt[["SO MPA prior pp_check (Machine)"]])

```

Model fit and QC:

```{r machine_so_mpa_model_summary, echo=FALSE, fig.width = 10}

std.fit <-  update(std.prior, 
                   sample_prior = "yes",
                   control = list(adapt_delta=0.9999),
                   seed = my.seed, 
                   cores = my.cores,
                   file = paste0(rds_folder_name, "so_model_summary_machine.rds"),
                   file_refit = "on_change")
summary(std.fit)

```

## MPA: MCMC conversion diagnostics

Posterior predictive check

```{r machine_so_mpa_MCMC_ppcheck}

set.seed(2) # reproducible pp_check

plt[["SO MPA pp_check (Machine)"]] <- pp_check(std.fit, ndraws = 21)

print(plt[["SO MPA pp_check (Machine)"]])

```

Autocorrelations

```{r machine_so_mpa_MCMC_ac}

plt[["SO MPA ac (Machine)"]] <- stan_ac(std.fit$fit)

print(plt[["SO MPA ac (Machine)"]])

```

## MPA: Estimated model marginals

Estimated model medians +- 95% HPDCI (HPDCI = highest posterior density continuous interval) as a table:

```{r machine_so_mpa_emm}

emm <- emmeans(std.fit, ~ Side:Time, transform = "response", nesting = NULL)

emm_show(emm)

```

Estimated model means as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r machine_so_mpa_emm_plot, echo=FALSE, fig.width = 8}

plt[["SO MPA emm (Machine)"]] <- emm %>% emm_inorder %>%
  ggplot(aes(y = fct_rev(interaction(Side, Time, sep=", ", drop=TRUE)), x = .value, fill = Side)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  # geom_vline(xintercept=threshold, linetype="dashed", color="black") +
  # geom_vline(xintercept=-threshold, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA (mm)")

print(plt[["SO MPA emm (Machine)"]])

```

Estimated model means as a median +- 95% HPDCI ("x" - mean values of measurements for each rat)

```{r points_machine_so_mpa_emm_plot, echo=FALSE, fig.width=8}

plt[["SO MPA emm (Machine) with Data Points"]] <- 
  plt[["SO MPA emm (Machine)"]] +
    geom_point(
      pch = 4,
      position = position_jitterdodge(dodge.width = 0.6, jitter.width = 0.6, seed = 2),
      data = {
        data_machine_SO %>%
          group_by(RatID, Time, Side) %>%
          summarise(.value = mean(MPA), .groups = "drop")
      },
      aes(x=.value, y = as.numeric(fct_rev(interaction(Side, Time, sep=", ", drop=TRUE)))+0.2))

print(plt[["SO MPA emm (Machine) with Data Points"]])

```

## MPA: Contrasts

Contrasts BI vs SS as a table:

```{r machine_so_mpa_contrasts}

emmc <- rbind(contrast(emm, simple = "Side", method = "revpairwise"),
              contrast(emm, simple = "Time", method = "consec"))

emm_show(emmc)

```

Contrasts BI vs SS as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r machine_so_mpa_plot, echo=FALSE, fig.width = 8}

plt[["SO MPA by Side (Machine)"]] <- emmc %>% emm_inorder %>% filter(Side == ".") %>%
  ggplot(aes( y = fct_rev(interaction(Time, contrast, sep=", ", drop=TRUE)), x=.value, fill=contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA in mm, contrast: L-SO vs R-SO")

print(plt[["SO MPA by Side (Machine)"]])

```

Contrasts "between time" as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r machine_so_mpa_by_time, echo=FALSE, fig.width = 8}

plt[["SO MPA by Time (Machine)"]] <- emmc %>% emm_inorder %>% filter(Time == ".") %>% 
  ggplot(aes(y = fct_rev(interaction(Side, contrast, sep=", ", drop=TRUE)), x = .value, fill = contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA in mm, contrast: Time")

print(plt[["SO MPA by Time (Machine)"]])

```

Contrasts BI vs SS as a table:

```{r machine_so_mpa_contrasts_3_15}

emmc <- rbind(contrast(emm, simple = "Side", method = "revpairwise"),
              contrast(emm, simple = "Time", method = "consec", reverse = TRUE))

emm_show(emmc)

```

Contrasts "between time" as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r machine_so_mpa_by_time_3_15, echo=FALSE, fig.width = 8}

plt[["SO MPA by Time 3h0m - 3h15m (Machine)"]] <- emmc %>% emm_inorder %>% filter(Time == ".") %>% 
  ggplot(aes(y = fct_rev(interaction(Side, contrast, sep=", ", drop=TRUE)), x = .value, fill = contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA in mm, contrast: Time")

print(plt[["SO MPA by Time 3h0m - 3h15m (Machine)"]])

```

Since "Left SO" is not significantly different from "Right SO" we can merge all sham rats into single "SO" group to test against "Left UBI" and "Right UBI".

# (Machine) Analyse L-UBI vs R-UBI vs SO(L+R)

## MPA: Student Model

Prior predictive check

```{r Machine_ubi_mpa_check_prior}

myname <- paste0(myname0, "_UBI_SO_MP")

std.prior <- brm(
  data = data_machine,
  family = student,
  MPA ~ 0 + Time:Trt3 + (1|RatID),
  prior = c(prior(student_t(3, 0, 10), class = "sigma"),
            prior(normal(0, 3), class = "b")),
  # control = list(adapt_delta=0.9),
  seed = my.seed, 
  chains = my.cores, 
  cores = my.cores, 
  iter = 4e4,
  sample_prior = "only",
  file = paste0(rds_folder_name, "ubi_check_prior_machine.rds"),
  file_refit = "on_change"
)

cond_eff <- conditional_effects(std.prior, 
                                "Trt3", 
                                method="fitted", 
                                conditions=make_conditions(data_machine, vars = c("Time")))

plt[["UBI MPA prior vs data (machine)"]] <- plot(cond_eff, 
                                       points = TRUE, 
                                       point_args = list(width = 0.1, shape="o", col="red"),
                                       plot=FALSE)[[1]] + 
                                  geom_hline(yintercept=0, linetype="dashed", color="black")

set.seed(2)
plt[["UBI MPA prior pp_check (machine)"]] <- pp_check(std.prior, ndraws = 11)

print(cond_eff[[1]])
print(plt[["UBI MPA prior vs data (machine)"]])
print(plt[["UBI MPA prior pp_check (machine)"]])

```

Model fit and QC:

```{r machine_ubi_mpa_model_summary, echo=FALSE, fig.width = 10}

std.fit <-  update(std.prior, 
                   sample_prior = "yes",
                   # control = list(adapt_delta=0.95),
                   seed = my.seed,
                   cores = my.cores,
                   file = paste0(rds_folder_name, "ubi_model_summary_machine.rds"),
                   file_refit = "on_change")
summary(std.fit)

```

## MPA: MCMC conversion diagnostics

Posterior predictive check

```{r machine_ubi_mpa_MCMC_ppcheck}

set.seed(2) # reproducible pp_check

plt[["UBI MPA pp_check (machine)"]] <- pp_check(std.fit, ndraws = 21)

print(plt[["UBI MPA pp_check (machine)"]])

```

Autocorrelations

```{r machine_ubi_mpa_MCMC_ac}

plt[["UBI MPA ac (machine)"]] <- stan_ac(std.fit$fit)

print(plt[["UBI MPA ac (machine)"]])

```

## MPA: Estimated model marginals

Estimated model medians +- 95% HPDCI (HPDCI = highest posterior density continuous interval) as a table:

```{r machine_ubi_mpa_emm}

emm <- emmeans(std.fit, ~ Trt3*Time, transform = "response", nesting = NULL)

emm_show(emm)

```

Estimated model means as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r machine_ubi_mpa_emm_plot, echo=FALSE, fig.width = 8}

plt[["UBI MPA emm (machine)"]] <- emm %>% emm_inorder %>%
  ggplot(aes(y = fct_rev(interaction(Trt3, Time, sep=", ", drop=TRUE)), x = .value, fill = Trt3)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept = 0, linetype="dashed", color="black") +
  # geom_vline(xintercept = threshold, linetype="dashed", color="black") +
  # geom_vline(xintercept = -threshold, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA (mm), UBI")

print(plt[["UBI MPA emm (machine)"]])

```


Estimated model means as a median +- 95% HPDCI ("x" - mean values of measurements for each rat)

```{r points_machine_ubi_mpa_emm_plot, echo=FALSE, fig.width=8}

plt[["UBI MPA emm (machine) with Data Points"]] <- 
  plt[["UBI MPA emm (machine)"]] +
    geom_point(
      pch = 4,
      position = position_jitterdodge(dodge.width = 0.6, jitter.width = 0.6, seed = 2),
      data = {
        data_machine %>%
          group_by(RatID, Time, Trt3) %>%
          summarise(.value = mean(MPA), .groups = "drop")
      },
      aes(x=.value, y = as.numeric(fct_rev(interaction(Trt3, Time, sep=", ", drop=TRUE)))+0.2))

print(plt[["UBI MPA emm (machine) with Data Points"]])

```

## MPA: Contrasts

Contrasts BI vs SS as a table:

```{r machine_ubi_mpa_contrasts}

emmc <- rbind(contrast(emm, simple = "Trt3", method = "revpairwise"),
              contrast(emm, simple = "Time", method = "consec"))

emm_show(emmc)

```

Contrasts BI vs SS as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r machine_ubi_mpa_plot, echo=FALSE, fig.width = 8}

plt[["UBI MPA by Trt3 (machine)"]] <- emmc %>% emm_inorder %>% filter(Trt3 == ".") %>%
  ggplot(aes( y = fct_rev(interaction(Time, contrast, sep=", ", drop=TRUE)), x=.value, fill=contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA in mm, contrast: SO vs RUBI VS LUBI")

print(plt[["UBI MPA by Trt3 (machine)"]])

```

Contrasts "between time" as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r machine_ubi_mpa_by_time, echo=FALSE, fig.width = 8}

plt[["UBI MPA by Time (machine)"]] <- emmc %>% emm_inorder %>% filter(Time == ".") %>% 
  ggplot(aes(y = fct_rev(interaction(Trt3, contrast, sep=", ", drop=TRUE)), x = .value, fill = Trt3)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA in mm, contrast: Time")

print(plt[["UBI MPA by Time (machine)"]])

```

Contrasts BI vs SS as a table:

```{r machine_ubi_mpa_contrasts_3_15}

emmc <- rbind(contrast(emm, simple = "Trt3", method = "revpairwise"),
              contrast(emm, simple = "Time", method = "consec", reverse = TRUE))

emm_show(emmc)

```

Contrasts "between time" as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r machine_ubi_mpa_by_time_3_15, echo=FALSE, fig.width = 8}

plt[["UBI MPA by Time 3h0m - 3h15m (machine)"]] <- emmc %>% emm_inorder %>% filter(Time == ".") %>% 
  ggplot(aes(y = fct_rev(interaction(Trt3, contrast, sep=", ", drop=TRUE)), x = .value, fill = Trt3)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA in mm, contrast: Time")

print(plt[["UBI MPA by Time 3h0m - 3h15m (machine)"]])

```


Contrast of contrasts:

```{r machine_ubi_mpa_contrasts_of_contrasts}
emmc_2 <- contrast(emm, simple = "Trt3", method = "pairwise")
emmc_2 <- contrast(emmc_2, simple = "Time", method = "pairwise")
emm_show(emmc_2)

```

Contrast of contrasts as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r machine_ubi_mpa_by_time_of_contrasts, echo=FALSE, fig.width = 8}

plt[["UBI MPA 3h (LUBI–RUBI) vs 3h15m (LUBI–RUBI) (machine)"]] <- emmc_2 %>% emm_inorder %>% 
  ggplot(aes(y = fct_rev(interaction(contrast1, contrast, sep=", ", drop=TRUE)), x = .value, fill = contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA in mm, Contrast of contrasts")

print(plt[["UBI MPA 3h (LUBI–RUBI) vs 3h15m (LUBI–RUBI) (machine)"]])

```

Contrast of contrasts reverse:

```{r machine_ubi_mpa_contrasts_of_contrasts_reverse}
emmc_2 <- contrast(emm, simple = "Trt3", method = "revpairwise")
emmc_2 <- contrast(emmc_2, simple = "Time", method = "pairwise")
emm_show(emmc_2)

```

Contrast of contrasts as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r machine_ubi_mpa_by_time_of_contrasts_reverse, echo=FALSE, fig.width = 8}

plt[["UBI MPA 3h (LUBI–RUBI) vs 3h15m (LUBI–RUBI) (machine) reverse"]] <- emmc_2 %>% emm_inorder %>% 
  ggplot(aes(y = fct_rev(interaction(contrast1, contrast, sep=", ", drop=TRUE)), x = .value, fill = contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="MPA in mm, Contrast of contrasts")

print(plt[["UBI MPA 3h (LUBI–RUBI) vs 3h15m (LUBI–RUBI) (machine) reverse"]])

```

# Editable PowerPoint plots generated...

```{r pptx, message=TRUE, warning=TRUE, include=FALSE, results='hide'}

myname <- paste0(myname0, "_UBI_SO_Hand_Machine")

doc <- read_pptx()

for(nm in names(plt)) {
  doc <- doc %>%
    add_slide(layout = "Title and Content", master = "Office Theme") %>%
    ph_with(value = rvg::dml(ggobj = plt[[nm]]),
          location = ph_location_type(type = "body"
                                      #, width=S_width, height=S_height
                                      ),
          bg = "transparent" ) %>%
    ph_with(value = nm,
          location = ph_location_type(type = "title") )
}
doc %>% print(target = paste0(myname,".pptx"))

```