---
title: "Bilateral adrenalectomy: PAS (Pre, after adx, hand, machine)"
author: "Yaromir Kobikov <kobikov.yaromir@gmail.com>"
date: "9/23/2021"
output:
 word_document: default
 html_document:
  toc: true
  toc_float:
   collapsed: false
editor_options:
 chunk_output_type: inline
---

```{r setup, include=FALSE}
source("../BayesianPValue.R")
```

# PAS (Magnitude of Postural asymmetry)

Flex the right leg in “+”, and the left leg in “-“.

# Read Data

Read from Excel file.

```{r input}

rds_folder_name <- "../rds/bilateral_adrenalectomy/pas/"

file_name <- "../data/SemiAutoADX-masterfile-210807.xlsx"
sheet <- "MasterFile"

my.seed <- 103592321 # reproducible Bayessian fit

myname0 <- "PAS"

data <- 
  read_excel(file_name, sheet) %>%
  # filter(`Treatment 1` == "Spinalization") %>% 
  select(RatID, Operation, `Operation side`, `Measuerment method`, `Treatment 1`, starts_with(c("PA1.", "PA2.", "PA3."))) %>% 
  # mutate(PA3.6 = as.numeric(PA3.6)) %>%   
  pivot_longer(
    cols = PA1.1:PA3.6,
    names_to = c("Time"),
    names_pattern = "PA(.)",
    values_to = "PA"
  ) %>%
  mutate(RatID = factor(RatID),
         Side = factor(`Operation side`, c("Left", "Right"), c("L", "R")),
         Time = factor(Time, c("1", "2", "3"), c("0min", "15min", "180min")),
         
         Trt5 = ifelse(`Treatment 1` == "ADX", paste0(Side, `Treatment 1`), paste0(Side, Operation)),
         Trt5 = replace(Trt5, Operation == "SO", "SO"),
         Trt5 = factor(Trt5, c("SO", "LADX", "RADX", "LUBI", "RUBI"))
         ) %>%
  drop_na("PA") %>% 
  ungroup %>% droplevels(.)

data_hand <-
  data %>%
  filter(`Measuerment method` == "Hand") %>% 
  droplevels(.)

data_machine <-
  data %>%
  filter(`Measuerment method` == "MP") %>% 
  droplevels(.)

```

The group sizes are (distinct rats only, same rats with different stimulation locations are counted as duplicates)

```{r input2, echo=FALSE}

data %>% 
  arrange(Trt5, Time) %>% 
  group_by(Trt5, Time, `Measuerment method`) %>% 
  summarise(rats = length(unique(RatID)), .groups = "drop") %>%
  pivot_wider(names_from=c(Time), values_from=rats) %>% 
  replace_na(list("15min" = 0)) %>% 
  flextable %>% autofit

```


# (Hand) Analyse ADX: Pre-surgery (L + R) and 15 min after the ADX (L + R)

## PAS: Student Model

Prior predictive check

```{r hand_pas_adx_pre_after}

data_hand_ADX_pre_after <- 
  data_hand %>%
  filter(`Treatment 1` == "ADX") %>%
  filter(Time != "180min") %>% 
  droplevels(.)

myname <- paste0(myname0, "_adx_pre_after_Hand")

std.prior <- brm(
  data = data_hand_ADX_pre_after,
  family = student,
  PA ~ 0 + Time + (1|RatID),
  prior = c(prior(student_t(3, 0, 10), class = "sigma"),
            prior(normal(0, 3), class = "b")),
  seed = my.seed, 
  chains = my.cores, 
  cores = my.cores, 
  iter = 4e4,
  sample_prior = "only",
  file = paste0(rds_folder_name, "adx_pre_after_check_prior.rds"),
  file_refit = "on_change"
)

cond_eff <- conditional_effects(std.prior, 
                                "Time", 
                                method="fitted")

plt[["Pre vs After ADX: PAS prior vs data (hand)"]] <- plot(cond_eff, 
                                       points = TRUE, 
                                       point_args = list(width = 0.1, shape="o", col="red"),
                                       plot=FALSE)[[1]] + 
                                  geom_hline(yintercept=0, linetype="dashed", color="black")

set.seed(2)
plt[["Pre vs After ADX: PAS prior pp_check (hand)"]] <- pp_check(std.prior, ndraws = 11)

print(cond_eff[[1]])
print(plt[["Pre vs After ADX: PAS prior vs data (hand)"]])
print(plt[["Pre vs After ADX: PAS prior pp_check (hand)"]])


```

Model fit and QC:

```{r hand_pas_adx_pre_after_model_summary, echo=FALSE, fig.width = 10}

std.fit <-  update(std.prior, 
                   sample_prior = "yes",
                   control = list(adapt_delta = 0.99),
                   seed = my.seed, 
                   cores = my.cores,
                   file = paste0(rds_folder_name, "adx_pre_after_model_summary.rds"),
                   file_refit = "on_change")
summary(std.fit)

```

## PAS: MCMC conversion diagnostics

Posterior predictive check

```{r hand_pas_adx_pre_after_MCMC_ppcheck}

set.seed(2) # reproducible pp_check

plt[["Pre vs After ADX: PAS pp_check (hand)"]] <- pp_check(std.fit, ndraws = 21)

print(plt[["Pre vs After ADX: PAS pp_check (hand)"]])

```

Autocorrelations

```{r hand_pas_adx_pre_after_MCMC_ac}

plt[["Pre vs After ADX: PAS ac (hand)"]] <- stan_ac(std.fit$fit)

print(plt[["Pre vs After ADX: PAS ac (hand)"]])

```

## PAS: Estimated model marginals

Estimated model medians +- 95% HPDCI (HPDCI = highest posterior density continuous interval) as a table:

```{r hand_pas_adx_pre_after_emm}

emm <- emmeans(std.fit, ~ Time, transform = "response", nesting = NULL)
emm_show(emm)

```

Estimated model means as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_pas_adx_pre_after_emm_plot, echo=FALSE, fig.width = 8}

plt[["Pre vs After ADX: PAS emm (hand)"]] <- emm %>% emm_inorder %>%
  ggplot(aes(y = fct_rev(interaction(Time, drop=TRUE)), x = .value, fill = Time)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  # geom_vline(xintercept=threshold, linetype="dashed", color="black") +
  # geom_vline(xintercept=-threshold, linetype="dashed", color="black") +
  labs(title=myname, y="", x="PAS (mm) Pre-ADX and After-ADX")

print(plt[["Pre vs After ADX: PAS emm (hand)"]])

```

Estimated model means as a median +- 95% HPDCI ("x" - mean values of measurements for each rat)

```{r points_hand_pas_adx_pre_after_emm_plot, echo=FALSE, fig.width=8}

plt[["Pre vs After ADX: PAS emm (hand) with Data Points"]] <- 
  plt[["Pre vs After ADX: PAS emm (hand)"]] +
    geom_point(
      pch = 4,
      position = position_jitterdodge(dodge.width = 0.6, jitter.width = 0.6, seed = 2),
      data = {
        data_hand_ADX_pre_after %>%
          group_by(RatID, Time) %>%
          summarise(.value = mean(PA), .groups = "drop")
      },
      aes(x=.value, y = as.numeric(fct_rev(interaction(Time, drop=TRUE)))+0.2))

print(plt[["Pre vs After ADX: PAS emm (hand) with Data Points"]])

```

## PAS: Contrasts

Contrasts BI vs SS as a table:

```{r hand_pas_adx_pre_after_contrasts}

emmc <- contrast(emm, simple = "Time", method = "consec")

emm_show(emmc)

```

Contrasts "between time" as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_pas_adx_pre_after_by_time, echo=FALSE, fig.width = 8}

plt[["Pre vs After ADX: PAS by Time (hand)"]] <- emmc %>% emm_inorder %>% 
  ggplot(aes(y = fct_rev(interaction(contrast, drop=TRUE)), x = .value, fill = contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="PAS in mm, contrast: Time")

print(plt[["Pre vs After ADX: PAS by Time (hand)"]])

```

Contrasts BI vs SS as a table [0min - 15min]:

```{r hand_pas_adx_pre_after_contrasts_0_15}

emmc <- contrast(emm, simple = "Time", method = "consec", reverse = TRUE)

emm_show(emmc)

```

Contrasts "between time" as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_pas_adx_pre_after_by_time_0_15, echo=FALSE, fig.width = 8}

plt[["Pre vs After ADX: PAS by Time (hand) [0min - 15min]"]] <- emmc %>% emm_inorder %>% 
  ggplot(aes(y = fct_rev(interaction(contrast, drop=TRUE)), x = .value, fill = contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="PAS in mm, contrast: Time")

print(plt[["Pre vs After ADX: PAS by Time (hand) [0min - 15min]"]])

```


# (Hand) Analyse ADX: 15 min after the ADX and 3 hrs after the brain surgery, L vs R 

## PAS: Student Model

Prior predictive check

```{r hand_pas_adx_after_ubi}

data_hand_ADX_after_UBI <- 
  data_hand %>%
  filter(`Treatment 1` == "ADX") %>%
  filter(Time != "0min") %>% 
  droplevels(.) %>% 
  mutate(Trt3 = ifelse(Time == "15min", "ADX", paste0(Side, "UBI")),
         Trt3 = factor(Trt3, c("ADX", "LUBI", "RUBI")))

myname <- paste0(myname0, "_adx_after_ubi_Hand")

std.prior <- brm(
  data = data_hand_ADX_after_UBI,
  family = student,
  PA ~ 0 + Trt3 + (1|RatID),
  prior = c(prior(student_t(3, 0, 10), class = "sigma"),
            prior(normal(0, 3), class = "b")),
  seed = my.seed, 
  chains = my.cores, 
  cores = my.cores, 
  iter = 4e4,
  sample_prior = "only",
  file = paste0(rds_folder_name, "adx_after_ubi_check_prior.rds"),
  file_refit = "on_change"
)

cond_eff <- conditional_effects(std.prior, 
                                "Trt3", 
                                method="fitted")
                                # conditions=make_conditions(data_hand_ADX_after_UBI, vars = c("Time")))

plt[["After ADX vs UBI: PAS prior vs data (hand)"]] <- plot(cond_eff, 
                                       points = TRUE, 
                                       point_args = list(width = 0.1, shape="o", col="red"),
                                       plot=FALSE)[[1]] + 
                                  geom_hline(yintercept=0, linetype="dashed", color="black")

set.seed(2)
plt[["After ADX vs UBI: PAS prior pp_check (hand)"]] <- pp_check(std.prior, ndraws = 11)

print(cond_eff[[1]])
print(plt[["After ADX vs UBI: PAS prior vs data (hand)"]])
print(plt[["After ADX vs UBI: PAS prior pp_check (hand)"]])


```

Model fit and QC:

```{r hand_pas_adx_after_ubi_model_summary, echo=FALSE, fig.width = 10}

std.fit <-  update(std.prior, 
                   sample_prior = "yes",
                   # control = list(adapt_delta = 0.85),
                   seed = my.seed, 
                   cores = my.cores,
                   file = paste0(rds_folder_name, "adx_after_ubi_model_summary.rds"),
                   file_refit = "on_change")
summary(std.fit)

```

## PAS: MCMC conversion diagnostics

Posterior predictive check

```{r hand_pas_adx_after_ubi_MCMC_ppcheck}

set.seed(2) # reproducible pp_check

plt[["After ADX vs UBI: PAS pp_check (hand)"]] <- pp_check(std.fit, ndraws = 21)

print(plt[["After ADX vs UBI: PAS pp_check (hand)"]])

```

Autocorrelations

```{r hand_pas_adx_after_ubi_MCMC_ac}

plt[["After ADX vs UBI: PAS ac (hand)"]] <- stan_ac(std.fit$fit)

print(plt[["After ADX vs UBI: PAS ac (hand)"]])

```

## PAS: Estimated model marginals

Estimated model medians +- 95% HPDCI (HPDCI = highest posterior density continuous interval) as a table:

```{r hand_pas_adx_after_ubi_emm}

emm <- emmeans(std.fit, ~ Trt3, transform = "response", nesting = NULL)
emm_show(emm)

```

Estimated model means as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_pas_adx_after_ubi_emm_plot, echo=FALSE, fig.width = 8}

plt[["After ADX vs UBI: PAS emm (hand)"]] <- emm %>% emm_inorder %>%
  ggplot(aes(y = fct_rev(interaction(Trt3, drop=TRUE)), x = .value, fill = Trt3)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  # geom_vline(xintercept=threshold, linetype="dashed", color="black") +
  # geom_vline(xintercept=-threshold, linetype="dashed", color="black") +
  labs(title=myname, y="", x="PAS (mm) After-ADX and UBI-ADX")

print(plt[["After ADX vs UBI: PAS emm (hand)"]])

```

Estimated model means as a median +- 95% HPDCI ("x" - mean values of measurements for each rat)

```{r points_hand_pas_adx_after_ubi_emm_plot, echo=FALSE, fig.width=8}

plt[["After ADX vs UBI: PAS emm (hand) with Data Points"]] <- 
  plt[["After ADX vs UBI: PAS emm (hand)"]] +
    geom_point(
      pch = 4,
      position = position_jitterdodge(dodge.width = 0.6, jitter.width = 0.6, seed = 2),
      data = {
        data_hand_ADX_after_UBI %>%
          group_by(RatID, Trt3) %>%
          summarise(.value = mean(PA), .groups = "drop")
      },
      aes(x=.value, y = as.numeric(fct_rev(interaction(Trt3, drop=TRUE)))+0.2))

print(plt[["After ADX vs UBI: PAS emm (hand) with Data Points"]])

```

## PAS: Contrasts

Contrasts BI vs SS as a table:

```{r hand_pas_adx_after_ubi_contrasts}

emmc <- contrast(emm, simple = "Trt3", method = "revpairwise")

emm_show(emmc)

```

Contrasts BI vs SS as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_pas_adx_after_ubi_contrasts_by_trt, echo=FALSE, fig.width = 8}

plt[["After ADX vs UBI: PAS by Trt (hand)"]] <- emmc %>% emm_inorder %>%
  ggplot(aes( y = fct_rev(interaction(contrast, drop=TRUE)), x=.value, fill=contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="PAS in mm, contrast: After ADX [15min] vs R-UBI and L-UBI [180min]:")

print(plt[["After ADX vs UBI: PAS by Trt (hand)"]])

```

# (Hand) Analyse SO(L+R) vs ADX+(L-UBI) vs ADX+(R-UBI) vs L-UBI vs R-UBI at the point 180 min

## PAS: Student Model

Prior predictive check

```{r hand_so_adx_ubi_pas_check_prior}

data_hand_180min <- 
  data_hand %>% 
  filter(Time == "180min") %>%
  droplevels(.) 
  

myname <- paste0(myname0, "_so_adx_ubi_Hand")

std.prior <- brm(
  data = data_hand_180min,
  family = student,
  PA ~ 0 + Trt5 + (1|RatID),
  prior = c(prior(student_t(3, 0, 10), class = "sigma"),
            prior(normal(0, 3), class = "b")),
  # control = list(adapt_delta=0.9),
  seed = my.seed, 
  chains = my.cores, 
  cores = my.cores, 
  iter = 4e4,
  sample_prior = "only",
  file = paste0(rds_folder_name, "so_adx_ubi_check_prior.rds"),
  file_refit = "on_change"
)

cond_eff <- conditional_effects(std.prior, 
                                "Trt5", 
                                method="fitted")

plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS prior vs data (hand)"]] <- plot(cond_eff, 
                                       points = TRUE, 
                                       point_args = list(width = 0.1, shape="o", col="red"),
                                       plot=FALSE)[[1]] + 
                                  geom_hline(yintercept=0, linetype="dashed", color="black")

set.seed(2)
plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS prior pp_check (hand)"]] <- pp_check(std.prior, ndraws = 11)

print(cond_eff[[1]])
print(plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS prior vs data (hand)"]])
print(plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS prior pp_check (hand)"]])

```

Model fit and QC:

```{r hand_so_adx_ubi_pas_model_summary, echo=FALSE, fig.width = 10}

std.fit <-  update(std.prior, 
                   sample_prior = "yes",
                   # control = list(adapt_delta=0.95),
                   seed = my.seed, 
                   cores = my.cores,
                   file = paste0(rds_folder_name, "so_adx_ubi_model_summary.rds"),
                   file_refit = "on_change")
summary(std.fit)

```

## PAS: MCMC conversion diagnostics

Posterior predictive check

```{r hand_so_adx_ubi_pas_MCMC_ppcheck}

set.seed(2) # reproducible pp_check

plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS pp_check (hand)"]] <- pp_check(std.fit, ndraws = 21)

print(plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS pp_check (hand)"]])

```

Autocorrelations

```{r hand_so_adx_ubi_pas_MCMC_ac}

plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS ac (hand)"]] <- stan_ac(std.fit$fit)

print(plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS ac (hand)"]])

```

## PAS: Estimated model marginals

Estimated model medians +- 95% HPDCI (HPDCI = highest posterior density continuous interval) as a table:

```{r hand_so_adx_ubi_pas_emm}

emm <- emmeans(std.fit, ~ Trt5, transform = "response", nesting = NULL)
emm_show(emm)

```

Estimated model means as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_so_adx_ubi_pas_emm_plot, echo=FALSE, fig.width = 8}

plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS emm (hand)"]] <- emm %>% emm_inorder %>%
  ggplot(aes(y = fct_rev(interaction(Trt5, drop=TRUE)), x = .value, fill = Trt5)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept = 0, linetype="dashed", color="black") +
  # geom_vline(xintercept = threshold, linetype="dashed", color="black") +
  # geom_vline(xintercept = -threshold, linetype="dashed", color="black") +
  labs(title=myname, y="", x="PAS (mm), SO vs ADX+UBI vs UBI")

print(plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS emm (hand)"]])

```

Estimated model means as a median +- 95% HPDCI ("x" - mean values of measurements for each rat)

```{r points_hand_so_adx_ubi_pas_emm_plot, echo=FALSE, fig.width=8}

plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS emm (hand) with Data Points"]] <- 
  plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS emm (hand)"]] +
    geom_point(
      pch = 4,
      position = position_jitterdodge(dodge.width = 0.6, jitter.width = 0.6, seed = 2),
      data = {
        data_hand_180min %>%
          group_by(RatID, Trt5) %>%
          summarise(.value = mean(PA), .groups = "drop")
      },
      aes(x=.value, y = as.numeric(fct_rev(interaction(Trt5, drop=TRUE)))+0.2))

print(plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS emm (hand) with Data Points"]])

```

## PAS: Contrasts

Contrasts BI vs SS as a table:

```{r hand_so_adx_ubi_pas_contrasts}

emmc <- contrast(emm, simple = "Trt5", method = "revpairwise")

emm_show(emmc)

```

Contrasts BI vs SS as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_so_adx_ubi_pas_plot, echo=FALSE}

plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS by Trt (hand)"]] <- emmc %>% emm_inorder %>%
  ggplot(aes( y = fct_rev(interaction(contrast, sep=", ", drop=TRUE)), x=.value, fill=contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="PAS in mm, contrast: SO vs RUBI VS LUBI")

print(plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS by Trt (hand)"]])

```

# (Machine) Analyse ADX: Pre-surgery (L + R) and 15 min after the ADX (L + R)

## PAS: Student Model

Prior predictive check

```{r machine_pas_adx_pre_after}

data_machine_ADX_pre_after <- 
  data_machine %>%
  filter(`Treatment 1` == "ADX") %>%
  filter(Time != "180min") %>% 
  droplevels(.)

myname <- paste0(myname0, "_adx_pre_after_machine")

std.prior <- brm(
  data = data_machine_ADX_pre_after,
  family = student,
  PA ~ 0 + Time + (1|RatID),
  prior = c(prior(student_t(3, 0, 10), class = "sigma"),
            prior(normal(0, 3), class = "b")),
  seed = my.seed, 
  chains = my.cores, 
  cores = my.cores, 
  iter = 4e4,
  sample_prior = "only",
  file = paste0(rds_folder_name, "adx_pre_after_check_prior_machine.rds"),
  file_refit = "on_change"
)

cond_eff <- conditional_effects(std.prior, 
                                "Time", 
                                method="fitted")

plt[["Pre vs After ADX: PAS prior vs data (machine)"]] <- plot(cond_eff, 
                                       points = TRUE, 
                                       point_args = list(width = 0.1, shape="o", col="red"),
                                       plot=FALSE)[[1]] + 
                                  geom_hline(yintercept=0, linetype="dashed", color="black")

set.seed(2)
plt[["Pre vs After ADX: PAS prior pp_check (machine)"]] <- pp_check(std.prior, ndraws = 11)

print(cond_eff[[1]])
print(plt[["Pre vs After ADX: PAS prior vs data (machine)"]])
print(plt[["Pre vs After ADX: PAS prior pp_check (machine)"]])


```

Model fit and QC:

```{r machine_pas_adx_pre_after_model_summary, echo=FALSE, fig.width = 10}

std.fit <-  update(std.prior, 
                   sample_prior = "yes",
                   # control = list(adapt_delta = 0.99),
                   seed = my.seed, 
                   cores = my.cores,
                   file = paste0(rds_folder_name, "adx_pre_after_model_summary_machine.rds"),
                   file_refit = "on_change")
summary(std.fit)

```

## PAS: MCMC conversion diagnostics

Posterior predictive check

```{r machine_pas_adx_pre_after_MCMC_ppcheck}

set.seed(2) # reproducible pp_check

plt[["Pre vs After ADX: PAS pp_check (machine)"]] <- pp_check(std.fit, ndraws = 21)

print(plt[["Pre vs After ADX: PAS pp_check (machine)"]])

```

Autocorrelations

```{r machine_pas_adx_pre_after_MCMC_ac}

plt[["Pre vs After ADX: PAS ac (machine)"]] <- stan_ac(std.fit$fit)

print(plt[["Pre vs After ADX: PAS ac (machine)"]])

```

## PAS: Estimated model marginals

Estimated model medians +- 95% HPDCI (HPDCI = highest posterior density continuous interval) as a table:

```{r machine_pas_adx_pre_after_emm}

emm <- emmeans(std.fit, ~ Time, transform = "response", nesting = NULL)
emm_show(emm)

```

Estimated model means as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r machine_pas_adx_pre_after_emm_plot, echo=FALSE, fig.width = 8}

plt[["Pre vs After ADX: PAS emm (machine)"]] <- emm %>% emm_inorder %>%
  ggplot(aes(y = fct_rev(interaction(Time, drop=TRUE)), x = .value, fill = Time)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  # geom_vline(xintercept=threshold, linetype="dashed", color="black") +
  # geom_vline(xintercept=-threshold, linetype="dashed", color="black") +
  labs(title=myname, y="", x="PAS (mm) Pre-ADX and After-ADX")

print(plt[["Pre vs After ADX: PAS emm (machine)"]])

```

Estimated model means as a median +- 95% HPDCI ("x" - mean values of measurements for each rat)

```{r points_machine_pas_adx_pre_after_emm_plot, echo=FALSE, fig.width=8}

plt[["Pre vs After ADX: PAS emm (machine) with Data Points"]] <- 
  plt[["Pre vs After ADX: PAS emm (machine)"]] +
    geom_point(
      pch = 4,
      position = position_jitterdodge(dodge.width = 0.6, jitter.width = 0.6, seed = 2),
      data = {
        data_machine_ADX_pre_after %>%
          group_by(RatID, Time) %>%
          summarise(.value = mean(PA), .groups = "drop")
      },
      aes(x=.value, y = as.numeric(fct_rev(interaction(Time, drop=TRUE)))+0.2))

print(plt[["Pre vs After ADX: PAS emm (machine) with Data Points"]])

```

## PAS: Contrasts

Contrasts BI vs SS as a table:

```{r machine_pas_adx_pre_after_contrasts}

emmc <- contrast(emm, simple = "Time", method = "consec")

emm_show(emmc)

```

Contrasts "between time" as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r machine_pas_adx_pre_after_by_time, echo=FALSE, fig.width = 8}

plt[["Pre vs After ADX: PAS by Time (machine)"]] <- emmc %>% emm_inorder %>% 
  ggplot(aes(y = fct_rev(interaction(contrast, drop=TRUE)), x = .value, fill = contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="PAS in mm, contrast: Time")

print(plt[["Pre vs After ADX: PAS by Time (machine)"]])

```

Contrasts BI vs SS as a table [0min - 15min]:

```{r machine_pas_adx_pre_after_contrasts_0_15}

emmc <- contrast(emm, simple = "Time", method = "consec", reverse = TRUE)

emm_show(emmc)

```

Contrasts "between time" as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r machine_pas_adx_pre_after_by_time_0_15, echo=FALSE, fig.width = 8}

plt[["Pre vs After ADX: PAS by Time (machine) [0min - 15min]"]] <- emmc %>% emm_inorder %>% 
  ggplot(aes(y = fct_rev(interaction(contrast, drop=TRUE)), x = .value, fill = contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="PAS in mm, contrast: Time")

print(plt[["Pre vs After ADX: PAS by Time (machine) [0min - 15min]"]])

```


# (Machine) Analyse ADX: 15 min after the ADX and 3 hrs after the brain surgery, L vs R 

## PAS: Student Model

Prior predictive check

```{r machine_pas_adx_after_ubi}

data_machine_ADX_after_UBI <- 
  data_machine %>%
  filter(`Treatment 1` == "ADX") %>%
  filter(Time != "0min") %>% 
  droplevels(.) %>% 
  mutate(Trt3 = ifelse(Time == "15min", "ADX", paste0(Side, "UBI")),
         Trt3 = factor(Trt3, c("ADX", "LUBI", "RUBI")))

myname <- paste0(myname0, "_adx_after_ubi_machine")

std.prior <- brm(
  data = data_machine_ADX_after_UBI,
  family = student,
  PA ~ 0 + Trt3 + (1|RatID),
  prior = c(prior(student_t(3, 0, 10), class = "sigma"),
            prior(normal(0, 3), class = "b")),
  seed = my.seed, 
  chains = my.cores, 
  cores = my.cores, 
  iter = 4e4,
  sample_prior = "only",
  file = paste0(rds_folder_name, "adx_after_ubi_check_prior_machine.rds"),
  file_refit = "on_change"
)

cond_eff <- conditional_effects(std.prior, 
                                "Trt3", 
                                method="fitted")
                                # conditions=make_conditions(data_hand_ADX_after_UBI, vars = c("Time")))

plt[["After ADX vs UBI: PAS prior vs data (machine)"]] <- plot(cond_eff, 
                                       points = TRUE, 
                                       point_args = list(width = 0.1, shape="o", col="red"),
                                       plot=FALSE)[[1]] + 
                                  geom_hline(yintercept=0, linetype="dashed", color="black")

set.seed(2)
plt[["After ADX vs UBI: PAS prior pp_check (machine)"]] <- pp_check(std.prior, ndraws = 11)

print(cond_eff[[1]])
print(plt[["After ADX vs UBI: PAS prior vs data (machine)"]])
print(plt[["After ADX vs UBI: PAS prior pp_check (machine)"]])


```

Model fit and QC:

```{r machine_pas_adx_after_ubi_model_summary, echo=FALSE, fig.width = 10}

std.fit <-  update(std.prior, 
                   sample_prior = "yes",
                   # control = list(adapt_delta = 0.85),
                   seed = my.seed, 
                   cores = my.cores,
                   file = paste0(rds_folder_name, "adx_after_ubi_model_summary_machine.rds"),
                   file_refit = "on_change")
summary(std.fit)

```

## PAS: MCMC conversion diagnostics

Posterior predictive check

```{r machine_pas_adx_after_ubi_MCMC_ppcheck}

set.seed(2) # reproducible pp_check

plt[["After ADX vs UBI: PAS pp_check (machine)"]] <- pp_check(std.fit, ndraws = 21)

print(plt[["After ADX vs UBI: PAS pp_check (machine)"]])

```

Autocorrelations

```{r machine_pas_adx_after_ubi_MCMC_ac}

plt[["After ADX vs UBI: PAS ac (machine)"]] <- stan_ac(std.fit$fit)

print(plt[["After ADX vs UBI: PAS ac (machine)"]])

```

## PAS: Estimated model marginals

Estimated model medians +- 95% HPDCI (HPDCI = highest posterior density continuous interval) as a table:

```{r machine_pas_adx_after_ubi_emm}

emm <- emmeans(std.fit, ~ Trt3, transform = "response", nesting = NULL)
emm_show(emm)

```

Estimated model means as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r machine_pas_adx_after_ubi_emm_plot, echo=FALSE, fig.width = 8}

plt[["After ADX vs UBI: PAS emm (machine)"]] <- emm %>% emm_inorder %>%
  ggplot(aes(y = fct_rev(interaction(Trt3, drop=TRUE)), x = .value, fill = Trt3)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  # geom_vline(xintercept=threshold, linetype="dashed", color="black") +
  # geom_vline(xintercept=-threshold, linetype="dashed", color="black") +
  labs(title=myname, y="", x="PAS (mm) After-ADX and UBI-ADX")

print(plt[["After ADX vs UBI: PAS emm (machine)"]])

```

Estimated model means as a median +- 95% HPDCI ("x" - mean values of measurements for each rat)

```{r points_machine_pas_adx_after_ubi_emm_plot, echo=FALSE, fig.width=8}

plt[["After ADX vs UBI: PAS emm (machine) with Data Points"]] <- 
  plt[["After ADX vs UBI: PAS emm (machine)"]] +
    geom_point(
      pch = 4,
      position = position_jitterdodge(dodge.width = 0.6, jitter.width = 0.6, seed = 2),
      data = {
        data_machine_ADX_after_UBI %>%
          group_by(RatID, Trt3) %>%
          summarise(.value = mean(PA), .groups = "drop")
      },
      aes(x=.value, y = as.numeric(fct_rev(interaction(Trt3, drop=TRUE)))+0.2))

print(plt[["After ADX vs UBI: PAS emm (machine) with Data Points"]])

```

## PAS: Contrasts

Contrasts BI vs SS as a table:

```{r machine_pas_adx_after_ubi_contrasts}

emmc <- contrast(emm, simple = "Trt3", method = "revpairwise")

emm_show(emmc)

```

Contrasts BI vs SS as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r machine_pas_adx_after_ubi_contrasts_by_trt, echo=FALSE, fig.width = 8}

plt[["After ADX vs UBI: PAS by Trt (machine)"]] <- emmc %>% emm_inorder %>%
  ggplot(aes( y = fct_rev(interaction(contrast, drop=TRUE)), x=.value, fill=contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="PAS in mm, contrast: After ADX [15min] vs R-UBI and L-UBI [180min]:")

print(plt[["After ADX vs UBI: PAS by Trt (machine)"]])

```

# (Machine) Analyse SO(L+R) vs ADX+(L-UBI) vs ADX+(R-UBI) vs L-UBI vs R-UBI at the point 180 min

## PAS: Student Model

Prior predictive check

```{r machine_so_adx_ubi_pas_check_prior}

data_machine_180min <- 
  data_machine %>% 
  filter(Time == "180min") %>%
  droplevels(.) 
  

myname <- paste0(myname0, "_so_adx_ubi_machine")

std.prior <- brm(
  data = data_machine_180min,
  family = student,
  PA ~ 0 + Trt5 + (1|RatID),
  prior = c(prior(student_t(3, 0, 10), class = "sigma"),
            prior(normal(0, 3), class = "b")),
  # control = list(adapt_delta=0.9),
  seed = my.seed, 
  chains = my.cores, 
  cores = my.cores, 
  iter = 4e4,
  sample_prior = "only",
  file = paste0(rds_folder_name, "so_adx_ubi_check_prior_machine.rds"),
  file_refit = "on_change"
)

cond_eff <- conditional_effects(std.prior, 
                                "Trt5", 
                                method="fitted")

plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS prior vs data (machine)"]] <- plot(cond_eff, 
                                       points = TRUE, 
                                       point_args = list(width = 0.1, shape="o", col="red"),
                                       plot=FALSE)[[1]] + 
                                  geom_hline(yintercept=0, linetype="dashed", color="black")

set.seed(2)
plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS prior pp_check (machine)"]] <- pp_check(std.prior, ndraws = 11)

print(cond_eff[[1]])
print(plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS prior vs data (machine)"]])
print(plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS prior pp_check (machine)"]])

```

Model fit and QC:

```{r machine_so_adx_ubi_pas_model_summary, echo=FALSE, fig.width = 10}

std.fit <-  update(std.prior, 
                   sample_prior = "yes",
                   # control = list(adapt_delta=0.95),
                   seed = my.seed, 
                   cores = my.cores,
                   file = paste0(rds_folder_name, "so_adx_ubi_model_summary_machine.rds"),
                   file_refit = "on_change")
summary(std.fit)

```

## PAS: MCMC conversion diagnostics

Posterior predictive check

```{r machine_so_adx_ubi_pas_MCMC_ppcheck}

set.seed(2) # reproducible pp_check

plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS pp_check (machine)"]] <- pp_check(std.fit, ndraws = 21)

print(plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS pp_check (machine)"]])

```

Autocorrelations

```{r machine_so_adx_ubi_pas_MCMC_ac}

plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS ac (machine)"]] <- stan_ac(std.fit$fit)

print(plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS ac (machine)"]])

```

## PAS: Estimated model marginals

Estimated model medians +- 95% HPDCI (HPDCI = highest posterior density continuous interval) as a table:

```{r machine_so_adx_ubi_pas_emm}

emm <- emmeans(std.fit, ~ Trt5, transform = "response", nesting = NULL)
emm_show(emm)

```

Estimated model means as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r machine_so_adx_ubi_pas_emm_plot, echo=FALSE, fig.width = 8}

plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS emm (machine)"]] <- emm %>% emm_inorder %>%
  ggplot(aes(y = fct_rev(interaction(Trt5, drop=TRUE)), x = .value, fill = Trt5)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept = 0, linetype="dashed", color="black") +
  # geom_vline(xintercept = threshold, linetype="dashed", color="black") +
  # geom_vline(xintercept = -threshold, linetype="dashed", color="black") +
  labs(title=myname, y="", x="PAS (mm), SO vs ADX+UBI vs UBI")

print(plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS emm (machine)"]])

```

Estimated model means as a median +- 95% HPDCI ("x" - mean values of measurements for each rat)

```{r points_machine_so_adx_ubi_pas_emm_plot, echo=FALSE, fig.width=8}

plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS emm (machine) with Data Points"]] <- 
  plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS emm (machine)"]] +
    geom_point(
      pch = 4,
      position = position_jitterdodge(dodge.width = 0.6, jitter.width = 0.6, seed = 2),
      data = {
        data_machine_180min %>%
          group_by(RatID, Trt5) %>%
          summarise(.value = mean(PA), .groups = "drop")
      },
      aes(x=.value, y = as.numeric(fct_rev(interaction(Trt5, drop=TRUE)))+0.2))

print(plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS emm (machine) with Data Points"]])

```


## PAS: Contrasts

Contrasts BI vs SS as a table:

```{r machine_so_adx_ubi_pas_contrasts}

emmc <- contrast(emm, simple = "Trt5", method = "revpairwise")

emm_show(emmc)

```

Contrasts BI vs SS as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r machine_so_adx_ubi_pas_plot, echo=FALSE}

plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS by Trt (machine)"]] <- emmc %>% emm_inorder %>%
  ggplot(aes( y = fct_rev(interaction(contrast, sep=", ", drop=TRUE)), x=.value, fill=contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="PAS in mm, contrast: SO vs RUBI VS LUBI")

print(plt[["SO vs ADX+UBI vs UBI at the point 180 min: PAS by Trt (machine)"]])

```

# Editable PowerPoint plots generated...

```{r pptx, message=TRUE, warning=TRUE, include=FALSE, results='hide'}

myname <- paste0(myname0, "_ADX_Hand_Machine")

doc <- read_pptx()

for(nm in names(plt)) {
  doc <- doc %>%
    add_slide(layout = "Title and Content", master = "Office Theme") %>%
    ph_with(value = rvg::dml(ggobj = plt[[nm]]),
          location = ph_location_type(type = "body"
                                      #, width=S_width, height=S_height
                                      ),
          bg = "transparent" ) %>%
    ph_with(value = nm,
          location = ph_location_type(type = "title") )
}
doc %>% print(target = paste0(myname,".pptx"))

```
