---
title: "Bilateral adrenalectomy: p_Contra (Pre, after adx, ADX+UBI, hand, machine) "
author: "Yaromir Kobikov <kobikov.yaromir@gmail.com>"
date: "10/7/2021"
output:
 word_document: default
 html_document:
  toc: true
  toc_float:
   collapsed: false
editor_options:
 chunk_output_type: inline
---

```{r setup, include=FALSE}
source("../BayesianPValue.R")
```

# p_Contra (Probability of "ContraLateral Flexion") 

Threshold 1 mm.
<!-- , and threshold 2 as 2 mm. -->

# Read Data

Read from Excel file.

```{r input}


rds_folder_name <- "../rds/bilateral_adrenalectomy/pContra/"

file_name <- "../data/SemiAutoADX-masterfile-210807.xlsx"
sheet <- "MasterFile"

my.seed <- 103592321 # reproducible Bayessian fit
threshold <- 1.0001 # assymetry means > 0mm, i.e. no symmetric rats

myname0 <- "pContra"

data <- 
  read_excel(file_name, sheet) %>%
  select(RatID, Operation, `Operation side`, `Measuerment method`, `Treatment 1`, starts_with(c("PA1.", "PA2.", "PA3."))) %>%  
  pivot_longer(
    cols = PA1.1:PA3.6,
    names_to = c("Time"),
    names_pattern = "PA(.)",
    values_to = "PA"
  ) %>%
  mutate(RatID = factor(RatID),
         Side = factor(`Operation side`, c("Left", "Right"), c("L", "R")),
         Time = factor(Time, c("1", "2", "3"), c("0min", "15min", "180min")),
         
         Trt5 = ifelse(`Treatment 1` == "ADX", paste0(Side, `Treatment 1`), paste0(Side, Operation)),
         Trt5 = replace(Trt5, Operation == "SO", "SO"),
         Trt5 = factor(Trt5, c("SO", "LADX", "RADX", "LUBI", "RUBI")),
         
         MPA = abs(PA),
         ) %>%
 mutate(Sym = factor(MPA < threshold, c(TRUE, FALSE), c("Sym", "Asym")),
        Flex = factor(ifelse(Sym == "Sym", NA, 
                         ifelse(PA > 0, "RF", "LF")), c("RF", "LF") ),
        Lat = factor(ifelse(
          (Side=="L" & Flex=="LF") |
          (Side=="R" & Flex=="RF"), "Ipsi", "Contra"),
          c("Ipsi","Contra"))
        ) %>%
  drop_na("RatID", "Trt5", "Time", "PA", "Flex", "Lat") %>%
  ungroup %>% droplevels(.)


data_hand <-
  data %>%
  filter(`Measuerment method` == "Hand") %>% 
  droplevels(.)

data_machine <-
  data %>%
  filter(`Measuerment method` == "MP") %>% 
  droplevels(.)

```

The group sizes are (distinct rats only, same rats with different stimulation locations are counted as duplicates)

```{r input2, echo=FALSE}

data %>% 
  # filter(Time == "180min") %>% 
  arrange(Trt5, Time) %>% 
  group_by(Trt5, Time, `Measuerment method`) %>% 
  summarise(rats = length(unique(RatID)), .groups = "drop") %>%
  pivot_wider(names_from=c(Time), values_from=rats) %>% 
  replace_na(list("0min" = 0, "180min" = 0)) %>% 
  flextable %>% autofit

```

# (Hand) Analyse ADX+(L-UBI) vs ADX+(R-UBI) vs L-UBI vs R-UBI at the point 180 min

## p_Contra: Model Overview

The data points for "Lateralization"

```{r hand_adx_ubi_p_Lat_input, echo=FALSE}

data_hand <-
  data_hand %>% 
  filter(Operation == "UBI") %>% 
  mutate(Trt4 = factor(Trt5, c("LADX", "RADX", "LUBI", "RUBI"))) %>% 
  droplevels(.)

data_hand %>% 
  arrange(Trt4, Time, Lat) %>% 
  group_by(Trt4, Time, Lat) %>% 
  summarise(rats = length(unique(RatID)), .groups = "drop") %>%
  pivot_wider(names_from=c(Time), values_from=rats) %>%
  flextable %>% autofit

```


We add a reference 50/50 level to "ContraLateral Flexion" data: nContra contralateral flexions out on nTrials asymmetric rats.

```{r hand_adx_ubi_p_Contra_input, echo=FALSE}

myname <- paste0(myname0, "_ADX_UBI_Hand")

dtaLat <- data_hand %>% 
  filter(!is.na(Lat)) %>%
  filter(Operation != "SO") %>% 
  droplevels(.) %>% # caution: may kill "Ipsi" level
  arrange(Trt4, Time) %>% 
  group_by(Trt4, Time) %>% 
  mutate( Lat = as.integer(factor(Lat, c("Ipsi","Contra")))-1 ) %>%
  summarise(nContra = as.integer(sum(Lat)), 
            nTrials = n(), 
            .groups = "drop")

dta5050 <- dtaLat %>% 
  ungroup() %>% group_by(Time) %>%
  summarise( Trt4 = "50/50",
             nContra = as.integer( round(max(nTrials)/2 - 0.1)),
             nTrials = as.integer( 2*nContra ), 
             .groups = "drop" )

dta5050 <- bind_rows(dta5050, dtaLat) %>%
  mutate(Trt4 = fct_inorder(Trt4))

dta5050 %>% 
  pivot_longer(cols=c(nContra, nTrials), names_to = "counts") %>%
  pivot_wider(names_from=c(Time), values_from=c(value)) %>% 
  flextable %>% autofit

```

Model fit and QC:

```{r hand_adx_ubi_p_Contra_model_summary}

m.lat <- brm(
  data = dta5050, family = binomial,
  nContra | trials(nTrials) ~ 0 + Trt4,
  prior = c(prior(normal(0, 1), class = "b")),
  seed = my.seed, 
  chains = my.cores, 
  cores = my.cores, 
  iter = 4e4, 
  sample_prior = "yes",
  file = paste0(rds_folder_name, "adx_ubi_p_Contra_model_summary.rds"),
  file_refit = "on_change")

summary(m.lat)

```

## p_Contra: MCMC conversion diagnostics

Posterior predictive check

```{r hand_adx_ubi_p_Contra_MCMC_ppcheck}

tryCatch(print( plt[["hand_adx_ubi_p_Contra pp_check"]] <- pp_check(m.lat, ndraws = 21) ), error=function(e) "pp_check() failed")

```

Autocorrelations

```{r hand_adx_ubi_p_Contra_MCMC_ac}

print( plt[["hand_adx_ubi__p_Contra ac"]] <- stan_ac(m.lat$fit) )

```

## p_Contra: Estimated model marginals

Estimated model medians +- 95% HPDCI (HPDCI = highest posterior density continuous interval) as a table. P-values are for p_Contra > 0.

```{r hand_adx_ubi_p_Contra_emm}

emm <- emmeans(m.lat, ~ Trt4, transform = "response", nesting = NULL)
emm_show(emm)

```

Plot of medians +- 95% HPDCI:

```{r hand_adx_ubi_p_Contra_emm2, echo=FALSE, fig.width = 8}

plt[["hand_adx_ubi_p_Contra emm"]] <- emm %>% emm_inorder %>%
  ggplot(aes(y = fct_rev(interaction(Trt4, drop=TRUE)), x = .value, fill = Trt4)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0.5, linetype="dashed", color="black") +
  coord_cartesian(xlim = c(0, 1)) +
  labs(title=myname, y="", x="p_Contra")
print(plt[["hand_adx_ubi_p_Contra emm"]])

```

## p_Contra: Contrasts

Contrasts "between treatment and 50/50" as a table:

```{r hand_adx_ubi_p_Contra_contrasts}

emmc <- contrast(emm, simple="Trt4", method = "trt.vs.ctrl1")
emm_show(emmc)

```

Contrasts "between treatment and 50/50" as a median +- 95% HPDCI:

```{r hand_adx_ubi_p_Contra_by_Trt, echo=FALSE, fig.width = 8}

plt[["hand_adx_ubi_p_Contra by Trt"]] <- emmc %>% emm_inorder %>% 
  ggplot(aes(y = fct_rev(interaction(contrast, drop=TRUE)), x = .value, fill = contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  # coord_cartesian(ylim = c(-1, 1)) +
  labs(title=myname, y="", x="p_Contra, contrast: treatment vs 50/50")

print(plt[["hand_adx_ubi_p_Contra by Trt"]])

```

# (Machine) Analyse ADX+(L-UBI) vs ADX+(R-UBI) vs L-UBI vs R-UBI at the point 180 min

## p_Contra: Model Overview

The data points for "Lateralization"

```{r machine_adx_ubi_p_Lat_input, echo=FALSE}

data_machine <-
  data_machine %>% 
  filter(Operation == "UBI") %>% 
  mutate(Trt4 = factor(Trt5, c("LADX", "RADX", "LUBI", "RUBI"))) %>% 
  filter(Time == "180min") %>% 
  droplevels(.)

data_machine %>% 
  arrange(Trt4, Time, Lat) %>% 
  group_by(Trt4, Time, Lat) %>% 
  summarise(rats = length(unique(RatID)), .groups = "drop") %>%
  pivot_wider(names_from=c(Time), values_from=rats) %>%
  flextable %>% autofit

```


We add a reference 50/50 level to "ContraLateral Flexion" data: nContra contralateral flexions out on nTrials asymmetric rats.

```{r machine_adx_ubi_p_Contra_input, echo=FALSE}

myname <- paste0(myname0, "_ADX_UBI_machine")

dtaLat <- data_machine %>% 
  filter(!is.na(Lat)) %>%
  filter(Operation != "SO") %>% 
  droplevels(.) %>% # caution: may kill "Ipsi" level
  arrange(Trt4, Time) %>% 
  group_by(Trt4, Time) %>% 
  mutate( Lat = as.integer(factor(Lat, c("Ipsi","Contra")))-1 ) %>%
  summarise(nContra = as.integer(sum(Lat)), 
            nTrials = n(), 
            .groups = "drop")

dta5050 <- dtaLat %>% 
  ungroup() %>% group_by(Time) %>%
  summarise( Trt4 = "50/50",
             nContra = as.integer( round(max(nTrials)/2 - 0.1)),
             nTrials = as.integer( 2*nContra ), 
             .groups = "drop" )

dta5050 <- bind_rows(dta5050, dtaLat) %>%
  mutate(Trt4 = fct_inorder(Trt4))

dta5050 %>% 
  pivot_longer(cols=c(nContra, nTrials), names_to = "counts") %>%
  pivot_wider(names_from=c(Time), values_from=c(value)) %>% 
  flextable %>% autofit

```

Model fit and QC:

```{r machine_adx_ubi_p_Contra_model_summary}

m.lat <- brm(
  data = dta5050, family = binomial,
  nContra | trials(nTrials) ~ 0 + Trt4,
  prior = c(prior(normal(0, 1), class = "b")),
  seed = my.seed, 
  chains = my.cores, 
  cores = my.cores, 
  iter = 4e4, 
  sample_prior = "yes",
  file = paste0(rds_folder_name, "adx_ubi_p_Contra_model_summary_machine.rds"),
  file_refit = "on_change")

summary(m.lat)

```

## p_Contra: MCMC conversion diagnostics

Posterior predictive check

```{r machine_adx_ubi_p_Contra_MCMC_ppcheck}

tryCatch(print( plt[["machine_adx_ubi_p_Contra pp_check"]] <- pp_check(m.lat, ndraws = 21) ), error=function(e) "pp_check() failed")

```

Autocorrelations

```{r machine_adx_ubi_p_Contra_MCMC_ac}

print( plt[["machine_adx_ubi__p_Contra ac"]] <- stan_ac(m.lat$fit) )

```

## p_Contra: Estimated model marginals

Estimated model medians +- 95% HPDCI (HPDCI = highest posterior density continuous interval) as a table. P-values are for p_Contra > 0.

```{r machine_adx_ubi_p_Contra_emm}

emm <- emmeans(m.lat, ~ Trt4, transform = "response", nesting = NULL)
emm_show(emm)

```

Plot of medians +- 95% HPDCI:

```{r machine_adx_ubi_p_Contra_emm2, echo=FALSE, fig.width = 8}

plt[["machine_adx_ubi_p_Contra emm"]] <- emm %>% emm_inorder %>%
  ggplot(aes(y = fct_rev(interaction(Trt4, drop=TRUE)), x = .value, fill = Trt4)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0.5, linetype="dashed", color="black") +
  coord_cartesian(xlim = c(0, 1)) +
  labs(title=myname, y="", x="p_Contra")
print(plt[["machine_adx_ubi_p_Contra emm"]])

```

## p_Contra: Contrasts

Contrasts "between treatment and 50/50" as a table:

```{r machine_adx_ubi_p_Contra_contrasts}

emmc <- contrast(emm, simple="Trt4", method = "trt.vs.ctrl1")
emm_show(emmc)

```

Contrasts "between treatment and 50/50" as a median +- 95% HPDCI:

```{r machine_adx_ubi_p_Contra_by_Trt, echo=FALSE, fig.width = 8}

plt[["machine_adx_ubi_p_Contra by Trt"]] <- emmc %>% emm_inorder %>% 
  ggplot(aes(y = fct_rev(interaction(contrast, drop=TRUE)), x = .value, fill = contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  # coord_cartesian(ylim = c(-1, 1)) +
  labs(title=myname, y="", x="p_Contra, contrast: treatment vs 50/50")

print(plt[["machine_adx_ubi_p_Contra by Trt"]])

```

# Editable PowerPoint plots generated...

```{r pptx, message=TRUE, warning=TRUE, include=FALSE, results='hide'}

myname <- paste0(myname0, "_ADX_UBI_Hand_Machine")

doc <- read_pptx()

for(nm in names(plt)) {
  doc <- doc %>%
    add_slide(layout = "Title and Content", master = "Office Theme") %>%
    ph_with(value = rvg::dml(ggobj = plt[[nm]]),
          location = ph_location_type(type = "body"
                                      #, width=S_width, height=S_height
                                      ),
          bg = "transparent" ) %>%
    ph_with(value = nm,
          location = ph_location_type(type = "title") )
}

doc %>% print(target = paste0(myname, ".pptx"))

```
