---
title: "Bilateral rhizotomy. Analyse Pa UBI"
author: "Yaromir Kobikov <kobikov.yaromir@gmail.com>"
date: "10/27/2021"
output:
 word_document: default
 html_document:
  toc: true
  toc_float:
   collapsed: false
editor_options:
 chunk_output_type: inline
---

```{r setup, include=FALSE}
source("../../BayesianPValue.R")
```

# Pa (Probability of postural asymmetry)

Threshold 1 mm. <!-- , and threshold 2 as 2 mm. -->

# Read Data

Read from Excel file.

```{r input}

rds_folder_name <- "../../rds/bilateral_rhizotomy/pa/"

file_name <- "../../data/SemiAutoADX-masterfile-210807.xlsx"
sheet <- "MasterFile"

my.seed <- 103592321 # reproducible Bayessian fit
threshold <- 1.0001 # assymetry means > 0mm, i.e. no symmetric rats

myname0 <- "Pa"

data <- 
  read_excel(file_name, sheet) %>%
  filter(`Treatment 1` == "Spinalization") %>% 
  select(RatID, Operation, `Operation side`, `Measuerment method`, starts_with(c("PA3.", "PA4."))) %>% 
  mutate(PA3.6 = as.numeric(PA3.6)) %>% 
  filter(rowSums(is.na(.)) < 6) %>% 
  pivot_longer(
    cols = PA3.1:PA4.6,
    names_to = c("Time"),
    names_pattern = "PA(.)",
    values_to = "PA"
  ) %>%
  mutate(RatID = factor(RatID),
         Side = factor(`Operation side`, c("Left", "Right"), c("L", "R")),
         Time = factor(Time, c("3", "4"), c("3h0m", "3h15m")),
         Trt3 = paste0(Side, Operation),
         Trt3 = replace(Trt3, Operation == "SO", "SO"),
         Trt3 = factor(Trt3, c("SO", "LUBI", "RUBI")),
         MPA = abs(PA),
         Sym = factor(MPA < threshold, c(TRUE, FALSE), c("Sym", "Asym"))) %>%
  drop_na("PA", "Sym") %>% 
  ungroup %>% droplevels(.)

data_hand_UBI <-
  data %>%
  filter(`Measuerment method` == "Hand") %>%
  filter(Operation == 'UBI') %>% 
  droplevels(.)

data_machine_UBI <-
  data %>%
  filter(`Measuerment method` == "MP") %>%
  filter(Operation == 'UBI') %>% 
  droplevels(.)

```

\|PA\| $\leqslant$ 1mm (threshold) are defined as "Symmetric" (Sym) (\|PA\| - Average of all 6 measurements per rat)

# (Hand) Analyse L-UBI vs R-UBI

## Pa: Model Overview

The data points

```{r hand_ubi_data, echo=FALSE}

myname <- paste0(myname0, "_UBI_Hand")


# data_hand_UBI %>% 
#   arrange(Side, Time) %>% 
#   group_by(Sym, Side, Time) %>% 
#   summarise(rats = length(unique(RatID)), .groups = "drop") %>%
#   pivot_wider(names_from=c(Time), values_from=rats) %>%
#   replace_na(list("3h0m" = 0)) %>% 
#   flextable(col_keys = c("Sym", "Side", "3h0m", "3h15m")) %>% autofit

data_hand_UBI %>%
  arrange(Side, Time) %>%
  group_by(RatID, Side, Time) %>%
  summarise(Sym = factor(mean(MPA) < threshold, c(TRUE, FALSE), c("Sym", "Asym")), .groups = "drop") %>%
  group_by(Sym, Side, Time) %>%
  summarise(rats = length(unique(RatID)), .groups = "keep") %>%
  pivot_wider(names_from=c(Time), values_from=rats) %>%
  replace_na(list("3h0m" = 0)) %>% 
  flextable(col_keys = c("Sym", "Side", "3h0m", "3h15m")) %>% autofit

```

Trials and number of asymmetric rats for the UBI group

```{r hand_ubi_pa_asym, echo=FALSE}

dtaAsym <- data_hand_UBI %>% 
  arrange(Side, Time) %>% 
  group_by(Side, Time) %>% 
  mutate( Asym = as.integer(factor(Sym, c("Sym", "Asym"))) - 1 ) %>%
  summarise(nAsym = as.integer(sum(Asym)), 
            nTrials = n(), 
            .groups = "drop") %>%
  mutate(Side = fct_inorder(Side))

# dta5050 <- dtaAsym %>%
#   ungroup() %>% group_by(Time) %>%
#   summarise( Side = "50/50",
#              nAsym = as.integer( round(max(nTrials)/2 - 0.1)),
#              nTrials = as.integer( 2*nAsym ),
#              .groups = "drop" )
# 
# dta5050 <- bind_rows(dta5050, dtaAsym) %>%
#   mutate(Side = fct_inorder(Side))

dtaAsym %>% 
  pivot_longer(cols=c(nAsym, nTrials), names_to = "counts") %>%
  pivot_wider(names_from=c(Time), values_from=c(value)) %>% 
  flextable %>% autofit

```

Model fit and QC:

```{r hand_ubi_pa_model_summary}

m.lat <- brm(
  data = dtaAsym, 
  family = binomial,
  nAsym | trials(nTrials) ~ 0 + Side:Time,
  prior = c(prior(normal(0, 1), class = "b")),
  seed = my.seed, 
  chains = my.cores, 
  cores = my.cores, 
  iter = 4e4, 
  sample_prior = "yes",
  file = paste0(rds_folder_name, "ubi_Pa_model_summary.rds"),
  file_refit = "on_change")

summary(m.lat)

```

## Pa: MCMC conversion diagnostics

Posterior predictive check

```{r hand_ubi_pa_MCMC_ppcheck}

plt[["hand UBI Pa pp_check"]] <- pp_check(m.lat, ndraws = 11)

print(plt[["hand UBI Pa pp_check"]])
```

Autocorrelations

```{r hand_ubi_pa_MCMC_ac}

print( plt[["hand UBI Pa ac"]] <- stan_ac(m.lat$fit) )

```

## Pa: Estimated model marginals

Estimated model medians +- 95% HPDCI (HPDCI = highest posterior density continuous interval) as a table. P-values are for Pa \> 0.

```{r hand_ubi_pa_emm}

emm <- emmeans(m.lat, ~ Side | Time, transform = "response", nesting = NULL)
emm_show(emm)

```

Plot of medians +- 95% HPDCI:

```{r hand_ubi_pa_emm2, echo=FALSE, fig.width = 8}

plt[["Hand UBI Pa emm"]] <- emm %>% emm_inorder %>%
  ggplot(aes(y = fct_rev(interaction(Side, Time, sep=", ", drop=TRUE)), x = .value, fill = Side)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0.5, linetype="dashed", color="black") +
  coord_cartesian(xlim = c(0, 1)) +
  labs(title=myname, y="", x="Pa: L-UBI, R-UBI")

print(plt[["Hand UBI Pa emm"]])

```

## Pa: Contrasts

Contrasts between Side as a table:

```{r hand_so_pa_contrasts}

emmc <- rbind(contrast(emm, simple="Side", method = "revpairwise"),
              contrast(emm, simple="Time", method = "consec"))
emm_show(emmc)

```

Contrasts BI vs SS as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_ubi_pas_plot_side, echo=FALSE, fig.width = 8}

plt[["UBI PAS by Side (hand)"]] <- emmc %>% emm_inorder %>% filter(Side == ".") %>%
  ggplot(aes( y = fct_rev(interaction(Time, contrast, sep=", ", drop=TRUE)), x=.value, fill=contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="Pa, contrast: Side")

print(plt[["UBI PAS by Side (hand)"]])

```

Contrasts BI vs SS as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r hand_ubi_pas_plot_time, echo=FALSE, fig.width = 8}

plt[["UBI PAS by Time (hand)"]] <- emmc %>% emm_inorder %>% filter(Time == ".") %>%
  ggplot(aes( y = fct_rev(interaction(Side, contrast, sep=", ", drop=TRUE)), x=.value, fill=contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="Pa, contrast: Time")

print(plt[["UBI PAS by Time (hand)"]])

```

# (Machine) Analyse L-UBI vs R-UBI

## Pa: Model Overview

The data points

```{r machine_ubi_data, echo=FALSE}

myname <- paste0(myname0, "_UBI_Machine")


# data_machine_UBI %>% 
#   arrange(Side, Time) %>% 
#   group_by(Sym, Side, Time) %>% 
#   summarise(rats = length(unique(RatID)), .groups = "drop") %>%
#   pivot_wider(names_from=c(Time), values_from=rats) %>%
#   replace_na(list("3h0m" = 0)) %>% 
#   flextable(col_keys = c("Sym", "Side", "3h0m", "3h15m")) %>% autofit

data_machine_UBI %>%
  arrange(Side, Time) %>%
  group_by(RatID, Side, Time) %>%
  summarise(Sym = factor(mean(MPA) < threshold, c(TRUE, FALSE), c("Sym", "Asym")), .groups = "drop") %>%
  group_by(Sym, Side, Time) %>%
  summarise(rats = length(unique(RatID)), .groups = "keep") %>%
  pivot_wider(names_from=c(Time), values_from=rats) %>%
  replace_na(list("3h0m" = 0)) %>% 
  flextable(col_keys = c("Sym", "Side", "3h0m", "3h15m")) %>% autofit

```

Trials and number of asymmetric rats for the UBI group

```{r machine_ubi_pa_asym, echo=FALSE}

dtaAsym <- data_machine_UBI %>% 
  arrange(Side, Time) %>% 
  group_by(Side, Time) %>% 
  mutate( Asym = as.integer(factor(Sym, c("Sym", "Asym"))) - 1 ) %>%
  summarise(nAsym = as.integer(sum(Asym)), 
            nTrials = n(), 
            .groups = "drop") %>%
  mutate(Side = fct_inorder(Side))

# dta5050 <- dtaAsym %>%
#   ungroup() %>% group_by(Time) %>%
#   summarise( Side = "50/50",
#              nAsym = as.integer( round(max(nTrials)/2 - 0.1)),
#              nTrials = as.integer( 2*nAsym ),
#              .groups = "drop" )
# 
# dta5050 <- bind_rows(dta5050, dtaAsym) %>%
#   mutate(Side = fct_inorder(Side))

dtaAsym %>% 
  pivot_longer(cols=c(nAsym, nTrials), names_to = "counts") %>%
  pivot_wider(names_from=c(Time), values_from=c(value)) %>% 
  flextable %>% autofit

```

Model fit and QC:

```{r machine_ubi_pa_model_summary}

m.lat <- brm(
  data = dtaAsym, 
  family = binomial,
  nAsym | trials(nTrials) ~ 0 + Side:Time,
  prior = c(prior(normal(0, 1), class = "b")),
  seed = my.seed, 
  chains = my.cores, 
  cores = my.cores, 
  iter = 4e4, 
  sample_prior = "yes",
  file = paste0(rds_folder_name, "machine_ubi_Pa_model_summary.rds"),
  file_refit = "on_change")

summary(m.lat)

```

## Pa: MCMC conversion diagnostics

Posterior predictive check

```{r machine_ubi_pa_MCMC_ppcheck}

plt[["machine UBI Pa pp_check"]] <- pp_check(m.lat, ndraws = 11)

print(plt[["machine UBI Pa pp_check"]])
```

Autocorrelations

```{r machine_ubi_pa_MCMC_ac}

print( plt[["machine UBI Pa ac"]] <- stan_ac(m.lat$fit) )

```

## Pa: Estimated model marginals

Estimated model medians +- 95% HPDCI (HPDCI = highest posterior density continuous interval) as a table. P-values are for Pa \> 0.

```{r machine_ubi_pa_emm}

emm <- emmeans(m.lat, ~ Side | Time, transform = "response", nesting = NULL)
emm_show(emm)

```

Plot of medians +- 95% HPDCI:

```{r machine_ubi_pa_emm2, echo=FALSE, fig.width = 8}

plt[["machine UBI Pa emm"]] <- emm %>% emm_inorder %>%
  ggplot(aes(y = fct_rev(interaction(Side, Time, sep=", ", drop=TRUE)), x = .value, fill = Side)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0.5, linetype="dashed", color="black") +
  coord_cartesian(xlim = c(0, 1)) +
  labs(title=myname, y="", x="Pa: L-UBI, R-UBI")

print(plt[["machine UBI Pa emm"]])

```

## Pa: Contrasts

Contrasts between Side as a table:

```{r machine_so_pa_contrasts}

emmc <- rbind(contrast(emm, simple="Side", method = "revpairwise"),
              contrast(emm, simple="Time", method = "consec"))
emm_show(emmc)

```

Contrasts BI vs SS as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r machine_ubi_pas_plot_side, echo=FALSE, fig.width = 8}

plt[["UBI PAS by Side (machine)"]] <- emmc %>% emm_inorder %>% filter(Side == ".") %>%
  ggplot(aes( y = fct_rev(interaction(Time, contrast, sep=", ", drop=TRUE)), x=.value, fill=contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="Pa, contrast: Side")

print(plt[["UBI PAS by Side (machine)"]])

```

Contrasts BI vs SS as a median +- 95% HPDCI (HPDCI = highest posterior density continuous interval):

```{r machine_ubi_pas_plot_time, echo=FALSE, fig.width = 8}

plt[["UBI PAS by Time (machine)"]] <- emmc %>% emm_inorder %>% filter(Time == ".") %>%
  ggplot(aes( y = fct_rev(interaction(Side, contrast, sep=", ", drop=TRUE)), x=.value, fill=contrast)) %>%
  my.stat_eyeh() +
  geom_vline(xintercept=0, linetype="dashed", color="black") +
  labs(title=myname, y="", x="Pa, contrast: Time")

print(plt[["UBI PAS by Time (machine)"]])

```


# Editable PowerPoint plots generated...

```{r pptx, message=TRUE, warning=TRUE, include=FALSE, results='hide'}

myname <- paste0(myname0, "_UBI_Hand_Machine")

doc <- read_pptx()

for(nm in names(plt)) {
  doc <- doc %>%
    add_slide(layout = "Title and Content", master = "Office Theme") %>%
    ph_with(value = rvg::dml(ggobj = plt[[nm]]),
          location = ph_location_type(type = "body"
                                      #, width=S_width, height=S_height
                                      ),
          bg = "transparent" ) %>%
    ph_with(value = nm,
          location = ph_location_type(type = "title") )
}
doc %>% print(target = paste0(myname,".pptx"))

```
